---
title: "Flufftail Analysis on the Gribben et. al dataset"
output:
  html_document: default
  pdf_document: default
date: "2025-09-22"
---

```{r, message=FALSE, warning=FALSE}
library(Flufftail)
library(Seurat)
library(SeuratWrappers)
library(monocle3)
library(ClustAssess)
library(dplyr)
library(gprofiler2)
library(ggplot2)
library(ggrepel)
library(SeuratDisk)
library(anndataR)
set.seed(42)
```

Prepare seurat object for Python reading
Let’s begin by loading a pre-processed Seurat object, which is ready for clustering
 (the adjacency matrix has already been computed using Seurat’s FindNeighbors) and visualise the cell types/annotations.
and inspecting the data
```{r load_object, cache=FALSE}

# full <- readRDS("C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/GSE202379_SeuratObject_AllCells.rds")
# disease_order <- c(
#   "NASH with cirrhosis",
#   "NAFLD",
#   "NASH w/o cirrhosis",
#   "Healthy control",
#   "end stage"
# )

# meta <- full@meta.data %>%
#   mutate(Disease.status = factor(Disease.status, levels = disease_order))

# # Hepatocyte/Cholangiocyte composition within each disease
# meta %>%
#   filter(cell.annotation %in% c("Hepatocytes", "Cholangiocytes")) %>%
#   count(Disease.status, cell.annotation) %>%
#   group_by(Disease.status) %>%
#   mutate(percent = round(100 * n / sum(n), 2))

# # Disease composition of entire dataset
# meta %>%
#   count(Disease.status) %>%
#   mutate(percent = round(100 * n / sum(n), 2))

```

```{r load_object, cache=FALSE}
# DefaultAssay(full)
# dim(full[["RNA"]]) #31257 99809
# dim(full[["SCT"]]) #30117 99809
# # keep only the cells we're interested in
# cells_keep <- colnames(full)[
#   full$cell.annotation %in% c("Hepatocytes", "Cholangiocytes") &
#   full$Disease.status == "end stage"
# ]
# length(cells_keep) #25527
# seurat_object <- subset(full,cells = cells_keep)
# rm(full)

# #sce <- as.SingleCellExperiment(seurat_object)
# #write_h5ad(sce, "C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/GSE202379_filtered.h5ad")


# ## prepare sub-sample
# full_small <- DietSeurat(
#   seurat_object,
#   assays = "RNA",
#   counts = TRUE,
#   data = FALSE,
#   scale.data = FALSE,
#   dimreducs = NULL
# )

# # Plot the UMAP reduction to visualize cell annotations
# DimPlot(seurat_object, reduction="umap_harmony_t.0", group.by = "cell.annotation")

# ```

# Let's remove the bottom island to focus on the population with the hepatocyte-cholangocyte bridge.
# ```{r remove_island}
# # Remove bottom island - all below -6 on UMAP_2
# umap_df <- as.data.frame(seurat_object@reductions$umap_harmony_t.0@cell.embeddings)
# colnames(umap_df) <- c("UMAP_1", "UMAP_2")
# #cell_names_keep <- rownames(umap_df[umap_df$UMAP_2 > -6,]) #original
# cell_names_keep <- rownames(umap_df[umap_df$UMAP_1 > 4 & umap_df$UMAP_2 > -10, ])
# seurat_object <- subset(seurat_object, cells = cell_names_keep)
# DimPlot(seurat_object, reduction="umap_harmony_t.0", group.by = "cell.annotation")


# ```
# ```{r fuzzy_clustering_analysis}
# SaveSeuratRds(object = seurat_object, file = "C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/seurat_object.rds")
# writeLines(colnames(seurat_object), "C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/shared_cells.txt")
```

# Fuzzy clustering
We will conduct fuzzy clustering on this object by running the Louvain algorithm 50 times with different random seeds, across a range of resolution values (0.01, 0.05, 0.1, 0.15, 0.2).

```{r fuzzy_clustering_analysis}
seurat_object <- LoadSeuratRds(file = "C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/seurat_object.rds")

# # Get sample names
sample_names <- colnames(seurat_object)

# Extract adjacency matrix (SNN) from Seurat object
adj_matrix <- seurat_object@graphs$SCT_snn

# Run fuzzy clustering analysis
fuzzy_clust_analysis <- Flufftail::fuzzy_clustering_analysis(
    adj_matrix,
    sample_names = sample_names,
    n_repetitions = 30,
    algorithm = 1,
   resolution = c(0.01, 0.05, 0.1, 0.15, 0.2)
  )

# Visualise configurations, sorted by their ECC median.
plot_ecc_boxplots(fuzzy_clust_analysis$ecc_list, 5, select_highest = T)
```

Gribben et al. [1] aimed to characterize the bridge between cholangiocytes and hepatocytes and identify biphenotypic cells (i.e., fuzzy cells) 
which were found at the transition between the two cell types (for a reminder of the cell types UMAP refer to Figure in the previous section). 
In our fuzzy clustering analysis, three resolutions resulted in two clusters (0.01, 0.05, 0.1). We will select the 0.01, following the Keep-it-Simple principle.
Let's visualise the ECC and hard clusters (selected using marjority voting) across the samples for this clustering configuration.

```{r umap_ecc_hard_clusters}
# Plot UMAP on ECC and hard clusters
umap <- seurat_object@reductions$umap_harmony_t.0@cell.embeddings

#previously Louvain_0.01_2 - but empty for my sample
#chosen_config <- "Louvain_0.01_6" #similar to original tutorial
chosen_config <- "Louvain_0.05_7" #shows delimitation between hepatocyte celss
ecc <- fuzzy_clust_analysis$ecc_list[[chosen_config]]
hard_clusters <- fuzzy_clust_analysis$hard_clusters_list[[chosen_config]]

theme_large_text <- theme(
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 15),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 15)
  )


plot_umap(umap, ecc, "ECC", "ECC")

plot_umap(umap, hard_clusters, "hard clusters", "Hard Clusters")
```

We can see that using fuzzy clustering and the ECC evaluation metric we identified fuzzy cells at the transition between the two hard clusters (in line with Gribben et. al definition of biphenotypic cells). The membership degrees across all the cells can also be examined by checking the degree_matrices_list of the selected configuration.

```{r membership_degrees_k2}
# Check membership degree matrix for Louvain res=0.01 and k=2
###head(fuzzy_clust_analysis$degree_matrices_list[[chosen_config]])


## see most fuzzy cells
deg_mat <- fuzzy_clust_analysis$degree_matrices_list[[chosen_config]]

fuzzy_cells <- deg_mat %>%
  filter(
    if_any(
      -Cell,
      ~ . >= 0.4 & . <= 0.6
    )
  )

head(fuzzy_cells)


```

## Consensus matrix

Let's also check the consensus matrix using the `get_consensus_matrix` function. The resulting matrix can be visualized using the `subsample_consensus_mat_plot` function, which randomly subsamples the matrix to a specified number of cells (n_sample). This subsampling is necessary due to the computational intensity of visualizing the entire matrix in a heatmap.

```{r consensus_mat}
# Get consensus matrix
consensus <- get_consensus_matrix(fuzzy_clust_analysis$membership_lists[[chosen_config]], sample_names)

# Subsample and visualise - 2000 cells
consensus_plot <- subsample_consensus_mat_plot(consensus, n_sample = 2000)
consensus_plot$plot
```

The consensus shows that at resolution 0.01 with k = 2, clustering is highly stable, showing near-uniform blue on the diagonal indicating strong consensus and clear delineation between the two groups - samples reliably co-cluster with each other.

Despite the lack of instability we can apply Shannon's entropy function on the consensus matrix to identify any fuzzy cells. The rows (or columns, due to their symmetry) of the consensus matrix are treated as relative frequency distributions, where each entry $p_{ij}$ indicates the proportion of times cell $i$ clusters with cell $j$ across multiple clustering iterations. Shannon's entopy is defined as:

$$
H(p_i) = -\sum_{j} p_{ij} \log(p_{ij})
$$

where \( p\_{ij} \) represents the frequency that cell \( i \) co-clusters with cell \( j \). Cells exhibiting high entropy indicate higher instability, reflecting significant inconsistency in their co-clustering behaviour. Extremely fuzzy cells would result in the highest entropy as they have co-clustering probabilities between 0.25 and 0.5 with most other cells, signalling inconsistent co-clustering behaviour.

```{r entropy_consensus}
# Calculate and visualise entropy on the consensus matrix.

#entropy_consensus <- calculate_entropy(consensus)
#plot_umap(umap, entropy_consensus, "entropy", "Entropy on the Consensus Matrix")

# Subsample cells
cells_subset <- sample(rownames(consensus), 3000)

# Subset consensus
consensus_subset <- consensus[cells_subset, cells_subset]

# Compute entropy
entropy_consensus <- calculate_entropy(consensus_subset)

# Subset UMAP
umap_subset <- umap[cells_subset, ]

# Ensure same order
entropy_consensus <- entropy_consensus[rownames(umap_subset)]

# Plot
plot_umap(
    umap_subset,
    entropy_consensus,
    "entropy",
    "Entropy on the Consensus Matrix"
)


```

We can see again that the cells with the highest entropy (and thus most unreliable co-clustering behaviour with other cells) are mostly at the transitioning cells between the two clusters.


```{r}
entropy_membership <- calculate_entropy(fuzzy_clust_analysis$degree_matrices_list[[chosen_config]][,2:3]) # exclude cell name column
plot_umap(umap, entropy_membership, "entropy", "Entropy on the Membership Matrix")
```

# Pseudotime analysis

We will use the gene based mode of pseudotime analysis passing the following:

- Start and end genes: critical for setting the starting/ending positions of the pseudotime ordering. A biologist typically provides these genes or can be identified using the ClustAssess Shiny app [2].
- Distribution Threshold: Set the quantile threshold for each gene in the start and end gene sets, where a cell must express the gene above this quantile of its overall expression to be considered for pseudotime analysis. The threshold is calculated individually for each gene in the start and end gene sets.
- Number of Relax Genes: Specify the maximum number of genes that can fall below their respective quantile thresholds in a cell's expression profile for both the start and end gene sets. This flexibility allows for a certain number of genes to not meet the expression threshold, enabling the inclusion of the cell in the pseudotime analysis if the remaining genes meet their respective thresholds.

```{r pseudotime_analysis}
cds <- Flufftail::get_pseudotime_trajectory_inference(
  seurat_object,
  colnames(seurat_object),
  VariableFeatures(seurat_object),
  umap,
  start_genes = c("SERPINE1", "CYP2B6", "INSIG1", "HMGCS1"),
  start_relax_ngenes = 1,
  end_genes = c("CFTR", "RALYL", "KRT7", "ITGB8"),
  end_relax_ngenes = 1,
  threshold = 0.8
)

plot_cells(
  cds,
  color_cells_by = "pseudotime",
  label_cell_groups = FALSE,
  label_leaves = FALSE,
  label_branch_points = FALSE,
  graph_label_size = 1.5,
  label_roots = F,
  cell_size=0.8
)

pseudo_df <- data.frame(
  cell = colnames(cds),
  pseudotime = pseudotime(cds)
)
write.csv(pseudo_df, "C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/shared_pseudotime.csv")
```

A useful feature of Flufftail is the ability to get the decomposed pseudotime plot which visualises the distribution of cell types
 and clusters along the pseudotime axis (derived from the trajectory learned on all cells).

```{r decomposed_pseudotime, results='hide'}
# Ensure umap is a dataframe and the first two columns are named UMAP_1 and UMAP_2
umap_df <- as.data.frame(umap)
colnames(umap_df) <- c("UMAP_1", "UMAP_2")

umap_df$hard_clusters <- unlist(fuzzy_clust_analysis$hard_clusters_list[[chosen_config]])
umap_df_subsampled <- umap_df[colnames(cds), ]
pData(cds)$cell_type <- pData(cds)$cell.annotation

decomposed_pseudotime_plot <- get_decomposed_pseudotime_plot(cds, umap_df_subsampled$hard_clusters)

decomposed_pseudotime_plot$combined

# decomposed_pseudotime_plot$p2 + theme(
#     legend.title = element_text(size = 18),
#     legend.text = element_text(size = 15),
#     axis.title = element_text(size = 18),
#     axis.text = element_text(size = 18),
#     axis.text.x =  element_text(size=15)
#   )

```


The cells in cluster 1 display significantly lower pseudotime values and much narrower distribution compared to those in cluster 2. This highlights the sequential transition from cluster 1, representing Hepatocytes, to cluster 2, representing Cholangiocytes, over time.

# Find DE genes at the transition area
Researchers can identify clusters transitioning from one to another using the decomposed pseudotime plot and then use Flufftail to pinpoint genes differentially expressed specifically during the transition. In our case study, we only have two clusters, making the selection trivial; however, this technique can be applied to scenarios with multiple clusters.

The `get_transition_cells` function calculates the centroids of the two clusters of interest, and allows for a selection of a specific percentage of samples around these centroids. It also identifies the midpoint centroid—positioned between the two cluster centroids—which represents the transition area between clusters. The position of this midpoint centroid can be adjusted using the `x_y_translation` argument, and a defined number of cells surrounding this midpoint can be selected to represent the transitioning cells.

In this example, we select 40% of cells around the centroids of two clusters and 770 cells (purple colour) around the midpoint centroid, which I have shifted in UMAP coordinates by x = -0.8 and y = +1.1. The number of cells selected around the midpoint centroid should be adjusted based on the total number of samples in your dataset.

```{r transition_cells}
# Get cells at the transition between two clusters of interest and cells around the centroids of the two clusters.
transition_cells_results <- Flufftail::get_transition_cells(umap_df, clusters_of_interest = c(1,2), percentage_points_centroid = 0.4, x_y_translation = c(-0.8,1.1), num_points_transition = 770)
transition_cells_results$plot
```

**Important Note:** Our original analysis was performed in the package’s Shiny app, which enables biologists to interactively deselect cells for refinement. To replicate those results in R Markdown, we load the saved analysis object from the app and exclude the same cells before proceeding.

```{r reproducing_cells_app}
# Reading the analysis done using the shiny app. This is only to exclude the cells deselected at the bridge.
# flufftail_analysis_shiny_app <- readRDS("/Users/rafael/Downloads/flufftail_analysis_with_Rafael.rds")
# cells_excluded_from_shiny_app <- setdiff(
#   transition_cells_results$cells_at_transition,
#   flufftail_analysis_shiny_app$de_genes$closest_points_to_midpoint$cell
# )
# 
# # Update the list of transition cells after exclusion
# transition_cells_results$cells_at_transition <- setdiff(
#   transition_cells_results$cells_at_transition,
#   cells_excluded_from_shiny_app
# )
```

Now let's plot again the cells around each of the different states along with their centroids. 

```{r}
# Specify cell state
umap_df$state <- "other"
umap_df$state[rownames(umap_df) %in% transition_cells_results$centroids_cells[[1]]] <- "State A"
umap_df$state[rownames(umap_df) %in% transition_cells_results$centroids_cells[[2]]] <- "State B"
umap_df$state[rownames(umap_df) %in% transition_cells_results$cells_at_transition] <- "Transition"

default_colors <- scales::hue_pal()(3)
default_red <- default_colors[1]
default_blue <- default_colors[3]

plot_with_cell_states <- ggplot(umap_df, aes(x = UMAP_1, y = UMAP_2, color = state)) +
  geom_point(size = 1) +
  scale_color_manual(
    values = c(
      "other" = "gray80",
      "State A" = default_red,
      "State B" = default_blue,
      "Transition" = "purple"
    )
  ) +
  geom_point(data = transition_cells_results$centroid_results$midpoint_centroid, aes(x = centroid_UMAP_1, y = centroid_UMAP_2), color = "yellow", fill = "black", size = 5, shape = 23, stroke=2) +
  theme_classic() +
   geom_point(data = transition_cells_results$centroid_results$centroids, aes(x = centroid_UMAP_1, y = centroid_UMAP_2), color = "yellow", fill="black", size = 5, shape = 23, stroke=2) +
  labs(color = "Cell state")

plot_with_cell_states
```

Genes driving the transition are identified by subsetting the trajectory to include only the transitioning cells (colored purple) and using Monocle3’s `graph_test` function. The stringency of gene identification can be adjusted by modifying the q_value_thresh and morans_I_thresh. In this example, I opt for lenient values (q_value < 0.05, morans_I > 0.02) to identify a higher number of genes to be used for gene module clustering (see next section).

```{r de_genes_at_transition, echo=TRUE, results='hide'}
# Identify DE genes at the area where there are cells of transition.
DE_genes_results <- Flufftail::identify_DE_genes_at_the_transition(cds, transition_cells_results$cells_at_transition,  q_value_thresh=0.05, morans_I_thresh=0.02)

shared_genes <- intersect(
  DE_genes_results$test_results$gene_short_name,
  VariableFeatures(seurat_object)
)
writeLines(shared_genes, "C:/Users/Floarea/Desktop/corebioinfo/codes/flufftail/input_data/shared_genes.txt")

```

The gene expression of the top DE genes identified (sorted by descending Moran's I test value) across the pseudotime can be visualized in a heatmap.

```{r top_de_genes}
# Get top 25 DE genes at the transition - ranked by the morans I test.
top_DE_genes_transition <- DE_genes_results$test_results %>% arrange(desc(morans_I))
top_DE_genes_transition <- top_DE_genes_transition[1:20,]

# Assign the cell type to the seurat object.
seurat_object$cell_type <- seurat_object$cell.annotation

plot_top_DE_genes <- plot_DE_genes_heatmap(DE_genes_results$cds_sub, seurat_object@meta.data, top_DE_genes_transition$gene_short_name, 10)
plot_top_DE_genes

```

The plot shows the gene expression heatmap of the top 25 DE genes, enabling the identification of genes that are most expressed at different points of the transition.

We can also perform gene set enrichment analysis.

```{r gsea}
results <- gprofiler2::gost(
            query = subset(DE_genes_results$full_result)$gene_short_name,
            source = c("KEGG"),
            organism = "hsapiens",
            as_short_link = FALSE,
            evcodes = TRUE
          )

gsea_results <- results$result %>% arrange(desc(intersection_size))

head(gsea_results[,1:11])
```


```{r}
# Highlight top 5 by intersection size
top5 <- gsea_results %>% 
  slice(1:5)

p <- ggplot(gsea_results, aes(x = reorder(term_name, -log10(p_value)), 
                              y = -log10(p_value), 
                              size = intersection_size)) +
  geom_point(color = "grey70", alpha = 0.6) +
  geom_point(data = top5, aes(color = term_name), size = 4) +
  geom_text_repel(data = top5,
                  aes(label = term_name),
                  size = 5,                  # larger text for pathway labels
                  max.overlaps = Inf,
                  box.padding = 0.6,
                  segment.color = "grey60") +
  theme_classic() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16)
  ) +
  expand_limits(
    y = max(-log10(gsea_results$p_value)) + 1,
    x = c(0.5, nrow(gsea_results) + 5)
  ) +
  labs(x = "KEGG Pathways", y = "-log10(p-adj)") +
  guides(color = "none") 

p 

```
We can see that we were able to also identify the PI3K-Akt signaling pathway which as discussed by the paper is strongly associated with obesity and metabolic syndrome—both closely linked to MASLD.

Flufftail has two complementary strategies to study GRN dynamics: **data-driven hub discovery** approach and a **pathway-guided analysis**. 

The data-driven strategy (PATH 1) applies repeated community detection clustering on the transposed matrix of transitioning cells and DE genes (transitioning matrix) to reveal co-expression modules. Genes with low ECC across iterations, termed “fuzzy genes”, exhibit unstable module membership, suggesting flexible regulatory roles. Flufftail then prioritizes the fuzzy genes with strong network influence, nominating major regulatory hubs, such as transcription factors, that are likely to drive transcriptional rewiring. 

The pathway-guided strategy (PATH 2) begins with the gene set enrichment analysis (GSEA); once a pathway is selected, the GRN dynamics of selected genes within the pathway can be examined at the three different stages.

Both strategies converge in the construction of stage-specific GRNs to map regulatory rewiring across source, transition, and destination states.


# GRN dynamics - data-driven strategy (PATH 1)

## Fuzzy gene module clustering
Fuzzy gene module clustering can be performed on the pseudotime DE genes at the transition cells (identified above - transition_cells_results$cells_at_transition). The researcher can choose the resolution sequence (start, step, end), community-detection algorithm (1=Louvain, 2=Louvain-refined, 3=SLM, 4=Leiden), and the number of iterations for the fuzzy gene module clustering. 

Once the clustering finishes, a table reporting the number of partitions and a 5+1 figure ECC summary for each configuration (resolution, \(k\)) can be obtained using `get_summary_each_config_gene_modules`.

We will use SLM with 50 repetitions, trying different resolutions from 0.1 to 1.0 with 0.1 increments.

```{r gene_modules, message=FALSE}
scaled_matrix <- seurat_object@assays$SCT@scale.data

# Get matrix of cells at the transition and of genes influencing the transition (differentially expressed across the pseudotime at the transition area).
transition_matrix <- scaled_matrix[DE_genes_results$test_results$gene_short_name, transition_cells_results$cells_at_transition]

# Perform gene module clustering
gene_modules_clustering <- Flufftail::gene_modules_fuzzy_clustering(transition_matrix, nruns=50, resolution_list = seq(0.1, 1.0, 0.1), algorithm = 3)

# Get summary for each configuration (resolution, k).
summary_table <- get_summary_each_config_gene_modules(gene_modules_clustering)
print(summary_table)
```

We want to select a configuration based on the number of clusters we want that also has some fuzziness (to be able to identify fuzzy genes). For this example I am going to select partitions where resolution=0.5 and \(k\)=4 as it has a lot of stable cells (q75 ecc = 0.9586) but also some fuzziness (median ecc = 0.8517).

Let's check the degree matrix for this configuration.

```{r degree_matrix_gene_modules}
chosen_resolution_gene_mod <- "0.5"
chosen_k_gene_mod <- "4"
head(gene_modules_clustering$degree_matrix_list[[chosen_resolution_gene_mod]][[chosen_k_gene_mod]])
```
We can also examine the ECC and hard clusters UMAP plots.

```{r umap_gene_modules}
# Get umap of gene module clustering.
umap_gene_modules <- gene_modules_clustering$umap

# Get the ecc of a setting of interest.
ecc_gene_module <- gene_modules_clustering$element_consistency_list[[chosen_resolution_gene_mod]][[chosen_k_gene_mod]]
plot_umap(umap_gene_modules, ecc_gene_module, "ecc", "ECC gene modules")

# Get the hard clusters of a setting of interest.
hard_clusters_gene_module <- gene_modules_clustering$hard_clusters_list[[chosen_resolution_gene_mod]][[chosen_k_gene_mod]]
plot_hard_clusters_gene_modules <- plot_umap(umap_gene_modules, hard_clusters_gene_module, "hard clusters", title = "Hard clusters gene modules")
plot_hard_clusters_gene_modules
```

The `get_top_fuzzy_ranked` can be used to get top fuzzy genes based on ECC. In this example let's find the top 5% of genes with the lowest ECC.

```{r top_fuzzy_genes}
# Constuct a dataframe containing the genes and their corresponding ecc.
gene_modules_ecc_df <- data.frame(gene=rownames(umap_gene_modules), ecc=ecc_gene_module)
rownames(gene_modules_ecc_df) <- gene_modules_ecc_df$gene

# Get 5% of the most fuzzy genes on this clustering.
top_fuzzy_genes <- get_top_fuzzy_ranked(gene_modules_ecc_df, "ecc", 0.05)
top_fuzzy_genes
```

## Identifying major regulatory hubs

We can construct a GRN using GRNBoost2 [3], testing each top fuzzy gene as a transcription factor (TF). Top fuzzy genes with high co-variation of expression values (termed Importance by GRNBoost2) with many other genes are likely driving the dynamics and are thus potential gene regulatory hubs.

To use Flufftail's `get_GRN` function which internally uses GRNBoost2 we need to create a conda environment and install arboreto and pandas. I exported the Conda environment I used (please check the conda_environment folder on the GitHub repo) to a YAML file so that you can easily recreate the virtual environment.

```{r conda_env}
# library(reticulate)
# 
# 
# use_condaenv(
#   "base",
#   conda = "C:/Users/Floarea/miniconda3/Scripts/conda.exe",
#   required = TRUE
# )

# Activate conda environment. You need arboreto and pandas installed.
#use_condaenv("conda_env_package", required = TRUE)

# Export the Conda environment to a YAML file. You can create the exact same package as I have using: conda env create -f conda_env_package_environment.yml -n conda_env.
# py_run_string("
# import subprocess
# env_name = 'conda_env_package'
# output_file = env_name + '_environment.yml'
# subprocess.run(['conda', 'env', 'export', '--name', env_name, '--file', output_file])
# ")

# Import python packages.
# arboreto <- import("arboreto.algo")
# pd <- import("pandas")

# Simplify name to just grnboost2
#grnboost2 <- arboreto$grnboost2

grnboost2 <- algo$grnboost2


```

Let's construct the GRN and get the 5+1 figure summary of the Importance across all top fuzzy genes (will refer to this as global Importance).

```{r grn_global, results='hide'}
py_run_string("
import warnings
warnings.filterwarnings('ignore', category=UserWarning)
warnings.filterwarnings('ignore', category=FutureWarning)
")

grn_network_all_top_fuzzy <- get_GRN(transition_matrix, top_fuzzy_genes)
# 
# dim(transition_matrix)
# 
# length(top_fuzzy_genes)
# 
# 
# dim(transition_matrix)
# head(rownames(transition_matrix))
# head(colnames(transition_matrix))
# intersect(top_fuzzy_genes, colnames(transition_matrix))
# 
# get_GRN <- function(exp_matrix, tfs){
# 
#     if(length(tfs) == 1){
#         tfs <- c(tfs, "")
#     }
# 
#     exp_matrix <- t(exp_matrix)
# 
#     exp_matrix_pd <- pd$DataFrame(
#         data = as.matrix(exp_matrix),
#         index = rownames(exp_matrix),
#         columns = colnames(exp_matrix)
#     )
# 
#     tf_names_py <- r_to_py(tfs)
# 
#     py_seed <- reticulate::py_eval("int(42)")
# 
#     grn_network <- grnboost2(
#         expression_data = exp_matrix_pd,
#         tf_names = tf_names_py,
#         seed = py_seed
#     )
# 
#     return(grn_network)
# }
# 
# grn_network_all_top_fuzzy <- get_GRN(
#     as.matrix(transition_matrix),
#     c("HIF1A")
# )




```

```{r summary_grn}
# Get 5+1 figure summary of global Importance.
summary(grn_network_all_top_fuzzy$importance)

# Identify global median and third quartile importance.
global_median_importance <- median(grn_network_all_top_fuzzy$importance)
global_third_quartile_importance <- quantile(grn_network_all_top_fuzzy$importance, 0.75)
```

Now we can use the `get_summary_connections_per_gene_df` function to get for each gene the number of other genes with which it has an Importance value exceeding the global median and third quartile Importance. This highlights the genes most involved in the regulatory dynamics.

```{r connections_genes}
# Get number of connections per gene
summary_of_connections_per_gene_df <- Flufftail::get_summary_connections_per_gene_df(grn_network_all_top_fuzzy, top_fuzzy_genes)

# Get top 25 genes sorted by the number of genes above global third quartile of importance.
combined_ecc_with_summary_connections_df <- merge(gene_modules_ecc_df, summary_of_connections_per_gene_df, by = "gene")

sorted_connections_df_output <- combined_ecc_with_summary_connections_df %>% arrange(desc(percentage_genes_above_target_third_quartile_importance)) %>% select(gene, ecc, percentage_genes_above_target_median_importance, percentage_genes_above_target_third_quartile_importance) %>% head(25)

sorted_connections_df_output
```

Within the top 25 potential major regulatory hubs we have FGF13 (rank 2), CREB5 (rank 8), KLF6 (rank 20), SERPINE1 (rank 22) all of which were found by Gribben et al. to be upregulated in biphenotypic hepatocyte–cholangiocyte cells, thereby highlighting the potential of Flufftail to recover experimentally confirmed regulators.

We can highlight these genes on the UMAP to check where they are located.

```{r}
potential_major_regulatory_hubs <- c("KLF6", "SERPINE1", "CREB5", "FGF13")

highlight_df <- data.frame(
  UMAP_1 = umap_gene_modules[potential_major_regulatory_hubs, 1],
  UMAP_2 = umap_gene_modules[potential_major_regulatory_hubs, 2],
  gene   = potential_major_regulatory_hubs
)

plot_hard_clusters_gene_modules +
  geom_point(
    data = highlight_df,
    aes(UMAP_1, UMAP_2),
    color = "black",
    size = 2
  ) +
  geom_label_repel(
    data = highlight_df,
    aes(UMAP_1, UMAP_2, label = gene),
    color = "black",
    fill = "white",         
    label.size = 0.2,      
    box.padding = 0.4,     
    point.padding = 0.3,
    segment.color = "grey40",
    size = 8
  ) + theme_large_text + guides(
    color = guide_legend(
      override.aes = list(size = 6)   # make legend circles larger
    )
  )

```
Interestingly CREB5, KLF6, and SERPINE1 are all next to each other. FGF13 is relatively further away but still part of the same gene module cluster (hard cluster 3).

Let's check the expression of these four potential major regulatory hubs across the pseudotime.

```{r major_regulatory_hubs}
Flufftail::plot_genes_across_pseudotime(cds[potential_major_regulatory_hubs,], genes_to_plot=potential_major_regulatory_hubs) + theme_large_text
```

All four genes expression changes signficantly across the pseudotime. FGF13 expression exhibs a unimodal distribution along pseudotime, rising gradually from low levels in hepatocyte-like cells to a pronounced peak within the transition zone (pseudotime ≈ 5–8) before declining toward the cholangiocyte end state.

## GRN dynamics
Now let's examine the GRNs, setting them as hub genes at the three different states. We will specify as GRNBoost2 TFs the major regulatory hubs chosen above. The other genes in each of the input matrices are the DE genes identified earlier.

```{r grn_three_centroids,  results='hide'}
grns_path1 <- Flufftail::get_three_stage_GRNs(scaled_matrix, genes=DE_genes_results$test_results$gene_short_name, tfs = potential_major_regulatory_hubs, transition_cells_results = transition_cells_results, top_n = 5, importance_thresh=0.85)
```

The resulting GRNs for the three states/locations can be visualized individually at each step and combined, allowing for the examination of changes in regulatory topology and interaction strength. This provides detailed snapshots of GRNs across the transition, unveiling regulatory dynamics and advancing the researcher's understanding of the cellular transitions


```{r}
visualise_GRN(grns_path1$grn_list$grn_centroid_A, tfs= potential_major_regulatory_hubs, top_n = 5, importance_thresh=0.85)$plot
```

```{r}
visualise_GRN(grns_path1$grn_list$grn_centroid_transition, tfs= potential_major_regulatory_hubs, top_n = 5, importance_thresh=0.85)$plot
```

```{r}
visualise_GRN(grns_path1$grn_list$grn_centroid_B, tfs= potential_major_regulatory_hubs, top_n = 5, importance_thresh=0.85)$plot
```

We can also create a combined plot which highlights commonalities and differences.

```{r grn_combined_visualisation}
combined_grn <- create_combined_GRN(grn_1 = grns_path1$grn_plot_list$network_cluster_first, grn_mid = grns_path1$grn_plot_list$network_midpoint, grn_2 = grns_path1$grn_plot_list$network_cluster_second)

combined_grn
```


# GRN Dynamics - pathway-guided strategy (PATH 2)
Besides the data-driven route, Flufftail supports a pathway-guided analysis that starts from biologically curated gene sets and asks how regulatory wiring shifts across source → bridge → destination. 

Here we restrict GRN inference to pathway members present in our data and compare edges across the three stages. This path is a focused lens to expose **context-dependent rewiring** within a validated pathway.

Let's start by getting the genes of the PI3K–AKT pathway that are available in our scaled expression matrix.

```{r pi3k_genes, results='hide'}
# Get all PI3K–AKT pathway genes
pathway_genes <- gprofiler2::gconvert(
        query    = "KEGG:04151",       
        organism = "hsapiens"
      )$name


# Restrict to genes available in our (scaled) expression matrix
pi3k_genes <- intersect(pathway_genes, rownames(scaled_matrix))

head(pi3k_genes)
```

Now we can select any gene from this pathway and examine its top interactions with the rest of PI3K–AKT genes that are present in our dataset across the three GRN states.

## Example 1: IGF1-centric view within PI3K–AKT
For example, let's select the IGF1 gene, which is hepatocyte-enriched yet also supports biliary survival [2–4] and infer the three GRNs (one at each stage).

```{r, grn_igf1_example, results='hide'}
grns_path2_igf1 <- Flufftail::get_three_stage_GRNs(scaled_matrix = scaled_matrix, genes = pi3k_genes, tfs = "IGF1", transition_cells_results = transition_cells_results)

# Hepatocyte state
grns_path2_igf1$grn_plot_list$network_cluster_first$plot

# Bridging population state
grns_path2_igf1$grn_plot_list$network_midpoint$plot

# Cholangocyte state
grns_path2_igf1$grn_plot_list$network_cluster_second$plot

```

In the hepatocyte state (Cluster A), IGF1 shows strong inferred regulatory associations with EGFR-axis ligands (AREG, EREG), consistent with activation of regenerative signalling in cholestatic stress [5–7]. IGF1 is also linked with SPP1 (osteopontin), a factor upregulated in NASH that promotes chemokine secretion [8–10], suggesting hepatocyte-derived IGF1 may co-vary with inflammatory cues at the hepatocyte–cholangiocyte boundary. In the bridge state (Midpoint Cluster), IGF1’s strongest associations shift toward IL2RG, MAGI1, and FGF23. There is also a weaker but notable edge to **CREB5**. 

```{r igf1_creb5_expression, results='hide'}
major_regulatory_hubs_of_interest <- c("IGF1", "CREB5")
pseudo_fuzzy <- cds[major_regulatory_hubs_of_interest,]
Flufftail::plot_genes_across_pseudotime(pseudo_fuzzy, genes_to_plot=major_regulatory_hubs_of_interest)
```

Interestingly, when examining their expression across the pseudotime, we can see that IGF1 and CREB5 follow opposite expression trends: IGF1 declines steadily, while CREB5 increases toward the cholangiocyte end of the trajectory. This suggests a potential handover of regulatory influence, where IGF1 is most active early in hepatocyte-like cells and CREB5 becomes more prominent later in transitional states. 

This observation provides a rationale for testing both genes as transcription factor inputs in Flufftail’s pathway-guided GRN analysis, to evaluate whether they function as complementary or opposing regulators across states.

```{r}
grns_path2_igf1_creb5 <- Flufftail::get_three_stage_GRNs(scaled_matrix = scaled_matrix, genes = pi3k_genes, tfs = "IGF1", transition_cells_results = transition_cells_results)

# Hepatocyte state
grns_path2_igf1_creb5$grn_plot_list$network_cluster_first$plot

# Bridging population state
grns_path2_igf1_creb5$grn_plot_list$network_midpoint$plot

# Cholangocyte state
grns_path2_igf1_creb5$grn_plot_list$network_cluster_second$plot

```

## Example 2: Multiple genes of interest

Here is an example when selecting multiple genes of interest in the pathway.

```{r grn_igf1_creb5_example, results='hide'}
genes_of_interest_pathway <- c("IGF1", "CREB5", "PIK3R5", "PIK3CD", "BCL2", "COL4A1", "COL4A2")

# TODO: include in powerepoint both 0.85 and 0.9 thresh.
grns_path2_example <- Flufftail::get_three_stage_GRNs(scaled_matrix = scaled_matrix, genes = pi3k_genes, tfs = genes_of_interest_pathway, transition_cells_results = transition_cells_results, importance_thresh = 0.9, top_n = 10)
```

```{r}
visualise_GRN(grns_path2_example$grn_list$grn_centroid_A, tfs= genes_of_interest_pathway, top_n = 10, importance_thresh=0.9)$plot

visualise_GRN(grns_path2_example$grn_list$grn_centroid_transition, tfs= genes_of_interest_pathway, top_n = 10, importance_thresh=0.9)$plot

visualise_GRN(grns_path2_example$grn_list$grn_centroid_B, tfs= genes_of_interest_pathway, top_n = 10, importance_thresh=0.9)$plot
```

In the hepatocyte state, BCL2 connects with TNC and NGF, hinting at roles in matrix interaction and growth-factor response. IGF1 shows broad connectivity, linking to EGFR, FGF9, EPO, ITGA4, and EFNA1.

During the transition state, IGF1 loses these hepatocyte-specific links and instead associates with LPAR3, LPAR4, NR4A1, and CSF3R, reflecting a shift toward alternative signaling programs. Its influence contracts further in the cholangiocyte state, where IGF1 is no longer a central regulator.

ITGA4, which partners with IGF1 in the hepatocyte state, becomes strongly associated with BCL2 in the transition state. BCL2 also links to CREB5, a transcription factor that becomes prominent in the cholangiocyte network, where CREB5 connects with genes such as LAMA3, LPAR3, and EREG.

## References:
[1] Gribben, C., Galanakis, V., Calderwood, A., Williams, E. C., Chazarra-Gil, R., Larraz, M., Frau, C., Puengel, T., Guillot, A., Rouhani, F. J., Mahbubani, K., Godfrey, E., Davies, S. E., Athanasiadis, E., Saeb-Parsy, K., Tacke, F., Allison, M., Mohorianu, I., & Vallier, L. (2024). Acquisition of epithelial plasticity in human chronic liver disease. Nature, 630(8015), 166–173. https://doi.org/10.1038/s41586-024-07465-2

[2] Shahsavari, A., Munteanu, A., & Mohorianu, I. (2022). ClustAssess: tools for assessing the robustness of single-cell clustering. bioRxiv. https://doi.org/10.1101/2022.01.31.478592

Python set-up - before running anything else
```{r, message=FALSE, warning=FALSE}
library(reticulate)

use_condaenv(
  "conda_env_package",
  conda = "C:/Users/Floarea/miniconda3/Scripts/conda.exe",
  required = TRUE
)

py_config()

arboreto <- import("arboreto")
pd <- import("pandas")
algo <- import("arboreto.algo")
```
<!-- R Notebook saved outputs: do not edit
RNOTEBOOK_RMD_STATE_BEGIN
eyJ2ZXJzaW9uIjoyLCJjb2RlQ2VsbFN0YXRlcyI6W3siZmluZ2VycHJpbnQiOiJ7XCJsYW5ndWFnZVwiOlwiclwiLFwiY29kZVwi
OlwibGlicmFyeShGbHVmZnRhaWwpXFxyXFxubGlicmFyeShTZXVyYXQpXFxyXFxubGlicmFyeShTZXVyYXRXcmFwcGVycylcXHJc
XG5saWJyYXJ5KG1vbm9jbGUzKVxcclxcbmxpYnJhcnkoQ2x1c3RBc3Nlc3MpXFxyXFxubGlicmFyeShkcGx5cilcXHJcXG5saWJy
YXJ5KGdwcm9maWxlcjIpXFxyXFxubGlicmFyeShnZ3Bsb3QyKVxcclxcbmxpYnJhcnkoZ2dyZXBlbClcXHJcXG5saWJyYXJ5KFNl
dXJhdERpc2spXFxyXFxubGlicmFyeShhbm5kYXRhUilcXHJcXG5zZXQuc2VlZCg0MilcXHJcIixcIm9wdGlvbnNcIjp7XCJtZXNz
YWdlXCI6ZmFsc2UsXCJ3YXJuaW5nXCI6ZmFsc2V9fSIsInJlc3VsdCI6eyJ0eXBlIjoicmVzdWx0IiwiY2h1bmtfaWQiOiJjaHVu
ay0xIiwiY29uc29sZSI6InBhY2thZ2UgJ1NldXJhdCcgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuTG9hZGluZyBy
ZXF1aXJlZCBwYWNrYWdlOiBTZXVyYXRPYmplY3RcblxucGFja2FnZSAnU2V1cmF0T2JqZWN0JyB3YXMgYnVpbHQgdW5kZXIgUiB2
ZXJzaW9uIDQuNS4zXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IHNwXG5cbnBhY2thZ2UgJ3NwJyB3YXMgYnVpbHQgdW5kZXIg
UiB2ZXJzaW9uIDQuNS4zXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnU2V1cmF0T2JqZWN0J1xuXG5cblRoZSBmb2xsb3dpbmcgb2Jq
ZWN0IGlzIG1hc2tlZCBfYnlfICcuR2xvYmFsRW52JzpcblxuICAgICV8fCVcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJl
IG1hc2tlZCBmcm9tICdwYWNrYWdlOmJhc2UnOlxuXG4gICAgaW50ZXJzZWN0LCB0XG5cblxuXG5BdHRhY2hpbmcgcGFja2FnZTog
J1NldXJhdCdcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgX2J5XyAnLkdsb2JhbEVudic6XG5cbiAgICAlfHwl
XG5cblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBCaW9iYXNlXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogQmlvY0dl
bmVyaWNzXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogZ2VuZXJpY3NcblxuXG5BdHRhY2hpbmcgcGFja2FnZTogJ2dlbmVy
aWNzJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6YmFzZSc6XG5cbiAgICBhcy5k
aWZmdGltZSwgYXMuZmFjdG9yLCBhcy5vcmRlcmVkLCBpbnRlcnNlY3QsIGlzLmVsZW1lbnQsIHNldGRpZmYsXG4gICAgc2V0ZXF1
YWwsIHVuaW9uXG5cblxuXG5BdHRhY2hpbmcgcGFja2FnZTogJ0Jpb2NHZW5lcmljcydcblxuXG5UaGUgZm9sbG93aW5nIG9iamVj
dHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOnN0YXRzJzpcblxuICAgIElRUiwgbWFkLCBzZCwgdmFyLCB4dGFic1xuXG5cblRo
ZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6YmFzZSc6XG5cbiAgICBhbnlEdXBsaWNhdGVkLCBh
cGVybSwgYXBwZW5kLCBhcy5kYXRhLmZyYW1lLCBiYXNlbmFtZSwgY2JpbmQsXG4gICAgY29sbmFtZXMsIGRpcm5hbWUsIGRvLmNh
bGwsIGR1cGxpY2F0ZWQsIGV2YWwsIGV2YWxxLCBGaWx0ZXIsIEZpbmQsXG4gICAgZ2V0LCBncmVwLCBncmVwbCwgaXMudW5zb3J0
ZWQsIGxhcHBseSwgTWFwLCBtYXBwbHksIG1hdGNoLCBtZ2V0LFxuICAgIG9yZGVyLCBwYXN0ZSwgcG1heCwgcG1heC5pbnQsIHBt
aW4sIHBtaW4uaW50LCBQb3NpdGlvbiwgcmFuayxcbiAgICByYmluZCwgUmVkdWNlLCByb3duYW1lcywgc2FwcGx5LCBzYXZlUkRT
LCB0YWJsZSwgdGFwcGx5LCB1bmlxdWUsXG4gICAgdW5zcGxpdCwgd2hpY2gubWF4LCB3aGljaC5taW5cblxuXG5XZWxjb21lIHRv
IEJpb2NvbmR1Y3RvclxuXG4gICAgVmlnbmV0dGVzIGNvbnRhaW4gaW50cm9kdWN0b3J5IG1hdGVyaWFsOyB2aWV3IHdpdGhcbiAg
ICAnYnJvd3NlVmlnbmV0dGVzKCknLiBUbyBjaXRlIEJpb2NvbmR1Y3Rvciwgc2VlXG4gICAgJ2NpdGF0aW9uKFwiQmlvYmFzZVwi
KScsIGFuZCBmb3IgcGFja2FnZXMgJ2NpdGF0aW9uKFwicGtnbmFtZVwiKScuXG5cblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdl
OiBTaW5nbGVDZWxsRXhwZXJpbWVudFxuXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IFN1bW1hcml6ZWRFeHBlcmltZW50XG5c
bkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogTWF0cml4R2VuZXJpY3NcblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBtYXRy
aXhTdGF0c1xuXG5wYWNrYWdlICdtYXRyaXhTdGF0cycgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuXG5BdHRhY2hp
bmcgcGFja2FnZTogJ21hdHJpeFN0YXRzJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2th
Z2U6QmlvYmFzZSc6XG5cbiAgICBhbnlNaXNzaW5nLCByb3dNZWRpYW5zXG5cblxuXG5BdHRhY2hpbmcgcGFja2FnZTogJ01hdHJp
eEdlbmVyaWNzJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6bWF0cml4U3RhdHMn
OlxuXG4gICAgY29sQWxscywgY29sQW55TkFzLCBjb2xBbnlzLCBjb2xBdmdzUGVyUm93U2V0LCBjb2xDb2xsYXBzZSxcbiAgICBj
b2xDb3VudHMsIGNvbEN1bW1heHMsIGNvbEN1bW1pbnMsIGNvbEN1bXByb2RzLCBjb2xDdW1zdW1zLFxuICAgIGNvbERpZmZzLCBj
b2xJUVJEaWZmcywgY29sSVFScywgY29sTG9nU3VtRXhwcywgY29sTWFkRGlmZnMsXG4gICAgY29sTWFkcywgY29sTWF4cywgY29s
TWVhbnMyLCBjb2xNZWRpYW5zLCBjb2xNaW5zLCBjb2xPcmRlclN0YXRzLFxuICAgIGNvbFByb2RzLCBjb2xRdWFudGlsZXMsIGNv
bFJhbmdlcywgY29sUmFua3MsIGNvbFNkRGlmZnMsIGNvbFNkcyxcbiAgICBjb2xTdW1zMiwgY29sVGFidWxhdGVzLCBjb2xWYXJE
aWZmcywgY29sVmFycywgY29sV2VpZ2h0ZWRNYWRzLFxuICAgIGNvbFdlaWdodGVkTWVhbnMsIGNvbFdlaWdodGVkTWVkaWFucywg
Y29sV2VpZ2h0ZWRTZHMsXG4gICAgY29sV2VpZ2h0ZWRWYXJzLCByb3dBbGxzLCByb3dBbnlOQXMsIHJvd0FueXMsIHJvd0F2Z3NQ
ZXJDb2xTZXQsXG4gICAgcm93Q29sbGFwc2UsIHJvd0NvdW50cywgcm93Q3VtbWF4cywgcm93Q3VtbWlucywgcm93Q3VtcHJvZHMs
XG4gICAgcm93Q3Vtc3Vtcywgcm93RGlmZnMsIHJvd0lRUkRpZmZzLCByb3dJUVJzLCByb3dMb2dTdW1FeHBzLFxuICAgIHJvd01h
ZERpZmZzLCByb3dNYWRzLCByb3dNYXhzLCByb3dNZWFuczIsIHJvd01lZGlhbnMsIHJvd01pbnMsXG4gICAgcm93T3JkZXJTdGF0
cywgcm93UHJvZHMsIHJvd1F1YW50aWxlcywgcm93UmFuZ2VzLCByb3dSYW5rcyxcbiAgICByb3dTZERpZmZzLCByb3dTZHMsIHJv
d1N1bXMyLCByb3dUYWJ1bGF0ZXMsIHJvd1ZhckRpZmZzLCByb3dWYXJzLFxuICAgIHJvd1dlaWdodGVkTWFkcywgcm93V2VpZ2h0
ZWRNZWFucywgcm93V2VpZ2h0ZWRNZWRpYW5zLFxuICAgIHJvd1dlaWdodGVkU2RzLCByb3dXZWlnaHRlZFZhcnNcblxuXG5UaGUg
Zm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTpCaW9iYXNlJzpcblxuICAgIHJvd01lZGlhbnNcblxuXG5M
b2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IEdlbm9taWNSYW5nZXNcblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBzdGF0czRc
blxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBTNFZlY3RvcnNcblxucGFja2FnZSAnUzRWZWN0b3JzJyB3YXMgYnVpbHQgdW5k
ZXIgUiB2ZXJzaW9uIDQuNS4zXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnUzRWZWN0b3JzJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2Jq
ZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOnV0aWxzJzpcblxuICAgIGZpbmRNYXRjaGVzXG5cblxuVGhlIGZvbGxvd2luZyBv
YmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpiYXNlJzpcblxuICAgIGV4cGFuZC5ncmlkLCBJLCB1bm5hbWVcblxuXG5M
b2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IElSYW5nZXNcblxuXG5BdHRhY2hpbmcgcGFja2FnZTogJ0lSYW5nZXMnXG5cblxuVGhl
IGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20gJ3BhY2thZ2U6c3AnOlxuXG4gICAgJW92ZXIlXG5cblxuVGhlIGZvbGxv
d2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20gJ3BhY2thZ2U6Z3JEZXZpY2VzJzpcblxuICAgIHdpbmRvd3NcblxuXG5Mb2FkaW5n
IHJlcXVpcmVkIHBhY2thZ2U6IFNlcWluZm9cblxuXG5BdHRhY2hpbmcgcGFja2FnZTogJ1N1bW1hcml6ZWRFeHBlcmltZW50J1xu
XG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOlNldXJhdCc6XG5cbiAgICBBc3NheXNcblxu
XG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTpTZXVyYXRPYmplY3QnOlxuXG4gICAgQXNzYXlz
XG5cblxuXG5BdHRhY2hpbmcgcGFja2FnZTogJ21vbm9jbGUzJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2Vk
IGZyb20gJ3BhY2thZ2U6QmlvYmFzZSc6XG5cbiAgICBleHBycywgZkRhdGEsIGZEYXRhPC0sIHBEYXRhLCBwRGF0YTwtXG5cblxu
cGFja2FnZSAnQ2x1c3RBc3Nlc3MnIHdhcyBidWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcbnBhY2thZ2UgJ2RwbHlyJyB3YXMg
YnVpbHQgdW5kZXIgUiB2ZXJzaW9uIDQuNS4zXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnZHBseXInXG5cblxuVGhlIGZvbGxvd2lu
ZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpHZW5vbWljUmFuZ2VzJzpcblxuICAgIGludGVyc2VjdCwgc2V0ZGlm
ZiwgdW5pb25cblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTpTZXFpbmZvJzpcblxuICAg
IGludGVyc2VjdFxuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6SVJhbmdlcyc6XG5c
biAgICBjb2xsYXBzZSwgZGVzYywgaW50ZXJzZWN0LCBzZXRkaWZmLCBzbGljZSwgdW5pb25cblxuXG5UaGUgZm9sbG93aW5nIG9i
amVjdHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOlM0VmVjdG9ycyc6XG5cbiAgICBmaXJzdCwgaW50ZXJzZWN0LCByZW5hbWUs
IHNldGRpZmYsIHNldGVxdWFsLCB1bmlvblxuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdl
Om1hdHJpeFN0YXRzJzpcblxuICAgIGNvdW50XG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20gJ3BhY2th
Z2U6QmlvYmFzZSc6XG5cbiAgICBjb21iaW5lXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFj
a2FnZTpCaW9jR2VuZXJpY3MnOlxuXG4gICAgY29tYmluZSwgaW50ZXJzZWN0LCBzZXRkaWZmLCBzZXRlcXVhbCwgdW5pb25cblxu
XG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTpnZW5lcmljcyc6XG5cbiAgICBleHBsYWluXG5c
blxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpzdGF0cyc6XG5cbiAgICBmaWx0ZXIsIGxh
Z1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6YmFzZSc6XG5cbiAgICBpbnRlcnNl
Y3QsIHNldGRpZmYsIHNldGVxdWFsLCB1bmlvblxuXG5cbnBhY2thZ2UgJ2dwcm9maWxlcjInIHdhcyBidWlsdCB1bmRlciBSIHZl
cnNpb24gNC41LjNcbnBhY2thZ2UgJ2dncGxvdDInIHdhcyBidWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcbnBhY2thZ2UgJ2dn
cmVwZWwnIHdhcyBidWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcblJlZ2lzdGVyZWQgUzMgbWV0aG9kIG92ZXJ3cml0dGVuIGJ5
ICdTZXVyYXREaXNrJzpcbiAgbWV0aG9kICAgICAgICAgICAgZnJvbSAgXG4gIGFzLnNwYXJzZS5INUdyb3VwIFNldXJhdFxuIiwi
Y29uc29sZV9zZWdtZW50cyI6W3siY29kZSI6ImxpYnJhcnkoRmx1ZmZ0YWlsKSIsIm91dHB1dCI6IiJ9LHsiY29kZSI6ImxpYnJh
cnkoU2V1cmF0KSIsIm91dHB1dCI6InBhY2thZ2UgJ1NldXJhdCcgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuTG9h
ZGluZyByZXF1aXJlZCBwYWNrYWdlOiBTZXVyYXRPYmplY3RcblxucGFja2FnZSAnU2V1cmF0T2JqZWN0JyB3YXMgYnVpbHQgdW5k
ZXIgUiB2ZXJzaW9uIDQuNS4zXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IHNwXG5cbnBhY2thZ2UgJ3NwJyB3YXMgYnVpbHQg
dW5kZXIgUiB2ZXJzaW9uIDQuNS4zXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnU2V1cmF0T2JqZWN0J1xuXG5cblRoZSBmb2xsb3dp
bmcgb2JqZWN0IGlzIG1hc2tlZCBfYnlfICcuR2xvYmFsRW52JzpcblxuICAgICV8fCVcblxuXG5UaGUgZm9sbG93aW5nIG9iamVj
dHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOmJhc2UnOlxuXG4gICAgaW50ZXJzZWN0LCB0XG5cblxuXG5BdHRhY2hpbmcgcGFj
a2FnZTogJ1NldXJhdCdcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgX2J5XyAnLkdsb2JhbEVudic6XG5cbiAg
ICAlfHwlXG5cbiJ9LHsiY29kZSI6ImxpYnJhcnkoU2V1cmF0V3JhcHBlcnMpIiwib3V0cHV0IjoiIn0seyJjb2RlIjoibGlicmFy
eShtb25vY2xlMykiLCJvdXRwdXQiOiJMb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IEJpb2Jhc2VcblxuTG9hZGluZyByZXF1aXJl
ZCBwYWNrYWdlOiBCaW9jR2VuZXJpY3NcblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBnZW5lcmljc1xuXG5cbkF0dGFjaGlu
ZyBwYWNrYWdlOiAnZ2VuZXJpY3MnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpi
YXNlJzpcblxuICAgIGFzLmRpZmZ0aW1lLCBhcy5mYWN0b3IsIGFzLm9yZGVyZWQsIGludGVyc2VjdCwgaXMuZWxlbWVudCwgc2V0
ZGlmZixcbiAgICBzZXRlcXVhbCwgdW5pb25cblxuXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnQmlvY0dlbmVyaWNzJ1xuXG5cblRo
ZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6c3RhdHMnOlxuXG4gICAgSVFSLCBtYWQsIHNkLCB2
YXIsIHh0YWJzXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpiYXNlJzpcblxuICAg
IGFueUR1cGxpY2F0ZWQsIGFwZXJtLCBhcHBlbmQsIGFzLmRhdGEuZnJhbWUsIGJhc2VuYW1lLCBjYmluZCxcbiAgICBjb2xuYW1l
cywgZGlybmFtZSwgZG8uY2FsbCwgZHVwbGljYXRlZCwgZXZhbCwgZXZhbHEsIEZpbHRlciwgRmluZCxcbiAgICBnZXQsIGdyZXAs
IGdyZXBsLCBpcy51bnNvcnRlZCwgbGFwcGx5LCBNYXAsIG1hcHBseSwgbWF0Y2gsIG1nZXQsXG4gICAgb3JkZXIsIHBhc3RlLCBw
bWF4LCBwbWF4LmludCwgcG1pbiwgcG1pbi5pbnQsIFBvc2l0aW9uLCByYW5rLFxuICAgIHJiaW5kLCBSZWR1Y2UsIHJvd25hbWVz
LCBzYXBwbHksIHNhdmVSRFMsIHRhYmxlLCB0YXBwbHksIHVuaXF1ZSxcbiAgICB1bnNwbGl0LCB3aGljaC5tYXgsIHdoaWNoLm1p
blxuXG5cbldlbGNvbWUgdG8gQmlvY29uZHVjdG9yXG5cbiAgICBWaWduZXR0ZXMgY29udGFpbiBpbnRyb2R1Y3RvcnkgbWF0ZXJp
YWw7IHZpZXcgd2l0aFxuICAgICdicm93c2VWaWduZXR0ZXMoKScuIFRvIGNpdGUgQmlvY29uZHVjdG9yLCBzZWVcbiAgICAnY2l0
YXRpb24oXCJCaW9iYXNlXCIpJywgYW5kIGZvciBwYWNrYWdlcyAnY2l0YXRpb24oXCJwa2duYW1lXCIpJy5cblxuXG5Mb2FkaW5n
IHJlcXVpcmVkIHBhY2thZ2U6IFNpbmdsZUNlbGxFeHBlcmltZW50XG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogU3VtbWFy
aXplZEV4cGVyaW1lbnRcblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBNYXRyaXhHZW5lcmljc1xuXG5Mb2FkaW5nIHJlcXVp
cmVkIHBhY2thZ2U6IG1hdHJpeFN0YXRzXG5cbnBhY2thZ2UgJ21hdHJpeFN0YXRzJyB3YXMgYnVpbHQgdW5kZXIgUiB2ZXJzaW9u
IDQuNS4zXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnbWF0cml4U3RhdHMnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBt
YXNrZWQgZnJvbSAncGFja2FnZTpCaW9iYXNlJzpcblxuICAgIGFueU1pc3NpbmcsIHJvd01lZGlhbnNcblxuXG5cbkF0dGFjaGlu
ZyBwYWNrYWdlOiAnTWF0cml4R2VuZXJpY3MnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFj
a2FnZTptYXRyaXhTdGF0cyc6XG5cbiAgICBjb2xBbGxzLCBjb2xBbnlOQXMsIGNvbEFueXMsIGNvbEF2Z3NQZXJSb3dTZXQsIGNv
bENvbGxhcHNlLFxuICAgIGNvbENvdW50cywgY29sQ3VtbWF4cywgY29sQ3VtbWlucywgY29sQ3VtcHJvZHMsIGNvbEN1bXN1bXMs
XG4gICAgY29sRGlmZnMsIGNvbElRUkRpZmZzLCBjb2xJUVJzLCBjb2xMb2dTdW1FeHBzLCBjb2xNYWREaWZmcyxcbiAgICBjb2xN
YWRzLCBjb2xNYXhzLCBjb2xNZWFuczIsIGNvbE1lZGlhbnMsIGNvbE1pbnMsIGNvbE9yZGVyU3RhdHMsXG4gICAgY29sUHJvZHMs
IGNvbFF1YW50aWxlcywgY29sUmFuZ2VzLCBjb2xSYW5rcywgY29sU2REaWZmcywgY29sU2RzLFxuICAgIGNvbFN1bXMyLCBjb2xU
YWJ1bGF0ZXMsIGNvbFZhckRpZmZzLCBjb2xWYXJzLCBjb2xXZWlnaHRlZE1hZHMsXG4gICAgY29sV2VpZ2h0ZWRNZWFucywgY29s
V2VpZ2h0ZWRNZWRpYW5zLCBjb2xXZWlnaHRlZFNkcyxcbiAgICBjb2xXZWlnaHRlZFZhcnMsIHJvd0FsbHMsIHJvd0FueU5Bcywg
cm93QW55cywgcm93QXZnc1BlckNvbFNldCxcbiAgICByb3dDb2xsYXBzZSwgcm93Q291bnRzLCByb3dDdW1tYXhzLCByb3dDdW1t
aW5zLCByb3dDdW1wcm9kcyxcbiAgICByb3dDdW1zdW1zLCByb3dEaWZmcywgcm93SVFSRGlmZnMsIHJvd0lRUnMsIHJvd0xvZ1N1
bUV4cHMsXG4gICAgcm93TWFkRGlmZnMsIHJvd01hZHMsIHJvd01heHMsIHJvd01lYW5zMiwgcm93TWVkaWFucywgcm93TWlucyxc
biAgICByb3dPcmRlclN0YXRzLCByb3dQcm9kcywgcm93UXVhbnRpbGVzLCByb3dSYW5nZXMsIHJvd1JhbmtzLFxuICAgIHJvd1Nk
RGlmZnMsIHJvd1Nkcywgcm93U3VtczIsIHJvd1RhYnVsYXRlcywgcm93VmFyRGlmZnMsIHJvd1ZhcnMsXG4gICAgcm93V2VpZ2h0
ZWRNYWRzLCByb3dXZWlnaHRlZE1lYW5zLCByb3dXZWlnaHRlZE1lZGlhbnMsXG4gICAgcm93V2VpZ2h0ZWRTZHMsIHJvd1dlaWdo
dGVkVmFyc1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOkJpb2Jhc2UnOlxuXG4gICAg
cm93TWVkaWFuc1xuXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogR2Vub21pY1Jhbmdlc1xuXG5Mb2FkaW5nIHJlcXVpcmVk
IHBhY2thZ2U6IHN0YXRzNFxuXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IFM0VmVjdG9yc1xuXG5wYWNrYWdlICdTNFZlY3Rv
cnMnIHdhcyBidWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdTNFZlY3RvcnMnXG5cblxu
VGhlIGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20gJ3BhY2thZ2U6dXRpbHMnOlxuXG4gICAgZmluZE1hdGNoZXNcblxu
XG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOmJhc2UnOlxuXG4gICAgZXhwYW5kLmdyaWQs
IEksIHVubmFtZVxuXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogSVJhbmdlc1xuXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAn
SVJhbmdlcydcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTpzcCc6XG5cbiAgICAlb3Zl
ciVcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTpnckRldmljZXMnOlxuXG4gICAgd2lu
ZG93c1xuXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogU2VxaW5mb1xuXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnU3VtbWFy
aXplZEV4cGVyaW1lbnQnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20gJ3BhY2thZ2U6U2V1cmF0Jzpc
blxuICAgIEFzc2F5c1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOlNldXJhdE9iamVj
dCc6XG5cbiAgICBBc3NheXNcblxuXG5cbkF0dGFjaGluZyBwYWNrYWdlOiAnbW9ub2NsZTMnXG5cblxuVGhlIGZvbGxvd2luZyBv
YmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpCaW9iYXNlJzpcblxuICAgIGV4cHJzLCBmRGF0YSwgZkRhdGE8LSwgcERh
dGEsIHBEYXRhPC1cblxuIn0seyJjb2RlIjoibGlicmFyeShDbHVzdEFzc2VzcykiLCJvdXRwdXQiOiJwYWNrYWdlICdDbHVzdEFz
c2Vzcycgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuMyJ9LHsiY29kZSI6ImxpYnJhcnkoZHBseXIpIiwib3V0cHV0Ijoi
cGFja2FnZSAnZHBseXInIHdhcyBidWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdkcGx5
cidcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOkdlbm9taWNSYW5nZXMnOlxuXG4g
ICAgaW50ZXJzZWN0LCBzZXRkaWZmLCB1bmlvblxuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNr
YWdlOlNlcWluZm8nOlxuXG4gICAgaW50ZXJzZWN0XG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAn
cGFja2FnZTpJUmFuZ2VzJzpcblxuICAgIGNvbGxhcHNlLCBkZXNjLCBpbnRlcnNlY3QsIHNldGRpZmYsIHNsaWNlLCB1bmlvblxu
XG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6UzRWZWN0b3JzJzpcblxuICAgIGZpcnN0
LCBpbnRlcnNlY3QsIHJlbmFtZSwgc2V0ZGlmZiwgc2V0ZXF1YWwsIHVuaW9uXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMg
bWFza2VkIGZyb20gJ3BhY2thZ2U6bWF0cml4U3RhdHMnOlxuXG4gICAgY291bnRcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBp
cyBtYXNrZWQgZnJvbSAncGFja2FnZTpCaW9iYXNlJzpcblxuICAgIGNvbWJpbmVcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMg
YXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOkJpb2NHZW5lcmljcyc6XG5cbiAgICBjb21iaW5lLCBpbnRlcnNlY3QsIHNldGRpZmYs
IHNldGVxdWFsLCB1bmlvblxuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOmdlbmVyaWNz
JzpcblxuICAgIGV4cGxhaW5cblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOnN0YXRz
JzpcblxuICAgIGZpbHRlciwgbGFnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpi
YXNlJzpcblxuICAgIGludGVyc2VjdCwgc2V0ZGlmZiwgc2V0ZXF1YWwsIHVuaW9uXG5cbiJ9LHsiY29kZSI6ImxpYnJhcnkoZ3By
b2ZpbGVyMikiLCJvdXRwdXQiOiJwYWNrYWdlICdncHJvZmlsZXIyJyB3YXMgYnVpbHQgdW5kZXIgUiB2ZXJzaW9uIDQuNS4zIn0s
eyJjb2RlIjoibGlicmFyeShnZ3Bsb3QyKSIsIm91dHB1dCI6InBhY2thZ2UgJ2dncGxvdDInIHdhcyBidWlsdCB1bmRlciBSIHZl
cnNpb24gNC41LjMifSx7ImNvZGUiOiJsaWJyYXJ5KGdncmVwZWwpIiwib3V0cHV0IjoicGFja2FnZSAnZ2dyZXBlbCcgd2FzIGJ1
aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuMyJ9LHsiY29kZSI6ImxpYnJhcnkoU2V1cmF0RGlzaykiLCJvdXRwdXQiOiJSZWdpc3Rl
cmVkIFMzIG1ldGhvZCBvdmVyd3JpdHRlbiBieSAnU2V1cmF0RGlzayc6XG4gIG1ldGhvZCAgICAgICAgICAgIGZyb20gIFxuICBh
cy5zcGFyc2UuSDVHcm91cCBTZXVyYXRcbiJ9LHsiY29kZSI6ImxpYnJhcnkoYW5uZGF0YVIpIiwib3V0cHV0IjoiIn0seyJjb2Rl
Ijoic2V0LnNlZWQoNDIpIiwib3V0cHV0IjoiIn1dLCJzdGRvdXQiOiIiLCJzdGRlcnIiOiJwYWNrYWdlICdTZXVyYXQnIHdhcyBi
dWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogU2V1cmF0T2JqZWN0XG5cbnBhY2th
Z2UgJ1NldXJhdE9iamVjdCcgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdl
OiBzcFxuXG5wYWNrYWdlICdzcCcgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuXG5BdHRhY2hpbmcgcGFja2FnZTog
J1NldXJhdE9iamVjdCdcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgX2J5XyAnLkdsb2JhbEVudic6XG5cbiAg
ICAlfHwlXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpiYXNlJzpcblxuICAgIGlu
dGVyc2VjdCwgdFxuXG5cblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdTZXVyYXQnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMg
bWFza2VkIF9ieV8gJy5HbG9iYWxFbnYnOlxuXG4gICAgJXx8JVxuXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogQmlvYmFz
ZVxuXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IEJpb2NHZW5lcmljc1xuXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IGdl
bmVyaWNzXG5cblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdnZW5lcmljcydcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1h
c2tlZCBmcm9tICdwYWNrYWdlOmJhc2UnOlxuXG4gICAgYXMuZGlmZnRpbWUsIGFzLmZhY3RvciwgYXMub3JkZXJlZCwgaW50ZXJz
ZWN0LCBpcy5lbGVtZW50LCBzZXRkaWZmLFxuICAgIHNldGVxdWFsLCB1bmlvblxuXG5cblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdC
aW9jR2VuZXJpY3MnXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpzdGF0cyc6XG5c
biAgICBJUVIsIG1hZCwgc2QsIHZhciwgeHRhYnNcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1hc2tlZCBmcm9tICdw
YWNrYWdlOmJhc2UnOlxuXG4gICAgYW55RHVwbGljYXRlZCwgYXBlcm0sIGFwcGVuZCwgYXMuZGF0YS5mcmFtZSwgYmFzZW5hbWUs
IGNiaW5kLFxuICAgIGNvbG5hbWVzLCBkaXJuYW1lLCBkby5jYWxsLCBkdXBsaWNhdGVkLCBldmFsLCBldmFscSwgRmlsdGVyLCBG
aW5kLFxuICAgIGdldCwgZ3JlcCwgZ3JlcGwsIGlzLnVuc29ydGVkLCBsYXBwbHksIE1hcCwgbWFwcGx5LCBtYXRjaCwgbWdldCxc
biAgICBvcmRlciwgcGFzdGUsIHBtYXgsIHBtYXguaW50LCBwbWluLCBwbWluLmludCwgUG9zaXRpb24sIHJhbmssXG4gICAgcmJp
bmQsIFJlZHVjZSwgcm93bmFtZXMsIHNhcHBseSwgc2F2ZVJEUywgdGFibGUsIHRhcHBseSwgdW5pcXVlLFxuICAgIHVuc3BsaXQs
IHdoaWNoLm1heCwgd2hpY2gubWluXG5cblxuV2VsY29tZSB0byBCaW9jb25kdWN0b3JcblxuICAgIFZpZ25ldHRlcyBjb250YWlu
IGludHJvZHVjdG9yeSBtYXRlcmlhbDsgdmlldyB3aXRoXG4gICAgJ2Jyb3dzZVZpZ25ldHRlcygpJy4gVG8gY2l0ZSBCaW9jb25k
dWN0b3IsIHNlZVxuICAgICdjaXRhdGlvbihcIkJpb2Jhc2VcIiknLCBhbmQgZm9yIHBhY2thZ2VzICdjaXRhdGlvbihcInBrZ25h
bWVcIiknLlxuXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogU2luZ2xlQ2VsbEV4cGVyaW1lbnRcblxuTG9hZGluZyByZXF1
aXJlZCBwYWNrYWdlOiBTdW1tYXJpemVkRXhwZXJpbWVudFxuXG5Mb2FkaW5nIHJlcXVpcmVkIHBhY2thZ2U6IE1hdHJpeEdlbmVy
aWNzXG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogbWF0cml4U3RhdHNcblxucGFja2FnZSAnbWF0cml4U3RhdHMnIHdhcyBi
dWlsdCB1bmRlciBSIHZlcnNpb24gNC41LjNcblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdtYXRyaXhTdGF0cydcblxuXG5UaGUgZm9s
bG93aW5nIG9iamVjdHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOkJpb2Jhc2UnOlxuXG4gICAgYW55TWlzc2luZywgcm93TWVk
aWFuc1xuXG5cblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdNYXRyaXhHZW5lcmljcydcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMg
YXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOm1hdHJpeFN0YXRzJzpcblxuICAgIGNvbEFsbHMsIGNvbEFueU5BcywgY29sQW55cywg
Y29sQXZnc1BlclJvd1NldCwgY29sQ29sbGFwc2UsXG4gICAgY29sQ291bnRzLCBjb2xDdW1tYXhzLCBjb2xDdW1taW5zLCBjb2xD
dW1wcm9kcywgY29sQ3Vtc3VtcyxcbiAgICBjb2xEaWZmcywgY29sSVFSRGlmZnMsIGNvbElRUnMsIGNvbExvZ1N1bUV4cHMsIGNv
bE1hZERpZmZzLFxuICAgIGNvbE1hZHMsIGNvbE1heHMsIGNvbE1lYW5zMiwgY29sTWVkaWFucywgY29sTWlucywgY29sT3JkZXJT
dGF0cyxcbiAgICBjb2xQcm9kcywgY29sUXVhbnRpbGVzLCBjb2xSYW5nZXMsIGNvbFJhbmtzLCBjb2xTZERpZmZzLCBjb2xTZHMs
XG4gICAgY29sU3VtczIsIGNvbFRhYnVsYXRlcywgY29sVmFyRGlmZnMsIGNvbFZhcnMsIGNvbFdlaWdodGVkTWFkcyxcbiAgICBj
b2xXZWlnaHRlZE1lYW5zLCBjb2xXZWlnaHRlZE1lZGlhbnMsIGNvbFdlaWdodGVkU2RzLFxuICAgIGNvbFdlaWdodGVkVmFycywg
cm93QWxscywgcm93QW55TkFzLCByb3dBbnlzLCByb3dBdmdzUGVyQ29sU2V0LFxuICAgIHJvd0NvbGxhcHNlLCByb3dDb3VudHMs
IHJvd0N1bW1heHMsIHJvd0N1bW1pbnMsIHJvd0N1bXByb2RzLFxuICAgIHJvd0N1bXN1bXMsIHJvd0RpZmZzLCByb3dJUVJEaWZm
cywgcm93SVFScywgcm93TG9nU3VtRXhwcyxcbiAgICByb3dNYWREaWZmcywgcm93TWFkcywgcm93TWF4cywgcm93TWVhbnMyLCBy
b3dNZWRpYW5zLCByb3dNaW5zLFxuICAgIHJvd09yZGVyU3RhdHMsIHJvd1Byb2RzLCByb3dRdWFudGlsZXMsIHJvd1Jhbmdlcywg
cm93UmFua3MsXG4gICAgcm93U2REaWZmcywgcm93U2RzLCByb3dTdW1zMiwgcm93VGFidWxhdGVzLCByb3dWYXJEaWZmcywgcm93
VmFycyxcbiAgICByb3dXZWlnaHRlZE1hZHMsIHJvd1dlaWdodGVkTWVhbnMsIHJvd1dlaWdodGVkTWVkaWFucyxcbiAgICByb3dX
ZWlnaHRlZFNkcywgcm93V2VpZ2h0ZWRWYXJzXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20gJ3BhY2th
Z2U6QmlvYmFzZSc6XG5cbiAgICByb3dNZWRpYW5zXG5cblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBHZW5vbWljUmFuZ2Vz
XG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogc3RhdHM0XG5cbkxvYWRpbmcgcmVxdWlyZWQgcGFja2FnZTogUzRWZWN0b3Jz
XG5cbnBhY2thZ2UgJ1M0VmVjdG9ycycgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuXG5BdHRhY2hpbmcgcGFja2Fn
ZTogJ1M0VmVjdG9ycydcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTp1dGlscyc6XG5c
biAgICBmaW5kTWF0Y2hlc1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6YmFzZSc6
XG5cbiAgICBleHBhbmQuZ3JpZCwgSSwgdW5uYW1lXG5cblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBJUmFuZ2VzXG5cblxu
QXR0YWNoaW5nIHBhY2thZ2U6ICdJUmFuZ2VzJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNr
YWdlOnNwJzpcblxuICAgICVvdmVyJVxuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOmdy
RGV2aWNlcyc6XG5cbiAgICB3aW5kb3dzXG5cblxuTG9hZGluZyByZXF1aXJlZCBwYWNrYWdlOiBTZXFpbmZvXG5cblxuQXR0YWNo
aW5nIHBhY2thZ2U6ICdTdW1tYXJpemVkRXhwZXJpbWVudCdcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJv
bSAncGFja2FnZTpTZXVyYXQnOlxuXG4gICAgQXNzYXlzXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20g
J3BhY2thZ2U6U2V1cmF0T2JqZWN0JzpcblxuICAgIEFzc2F5c1xuXG5cblxuQXR0YWNoaW5nIHBhY2thZ2U6ICdtb25vY2xlMydc
blxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOkJpb2Jhc2UnOlxuXG4gICAgZXhwcnMs
IGZEYXRhLCBmRGF0YTwtLCBwRGF0YSwgcERhdGE8LVxuXG5cbnBhY2thZ2UgJ0NsdXN0QXNzZXNzJyB3YXMgYnVpbHQgdW5kZXIg
UiB2ZXJzaW9uIDQuNS4zXG5wYWNrYWdlICdkcGx5cicgd2FzIGJ1aWx0IHVuZGVyIFIgdmVyc2lvbiA0LjUuM1xuXG5BdHRhY2hp
bmcgcGFja2FnZTogJ2RwbHlyJ1xuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6R2Vu
b21pY1Jhbmdlcyc6XG5cbiAgICBpbnRlcnNlY3QsIHNldGRpZmYsIHVuaW9uXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMg
bWFza2VkIGZyb20gJ3BhY2thZ2U6U2VxaW5mbyc6XG5cbiAgICBpbnRlcnNlY3RcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMg
YXJlIG1hc2tlZCBmcm9tICdwYWNrYWdlOklSYW5nZXMnOlxuXG4gICAgY29sbGFwc2UsIGRlc2MsIGludGVyc2VjdCwgc2V0ZGlm
Ziwgc2xpY2UsIHVuaW9uXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3RzIGFyZSBtYXNrZWQgZnJvbSAncGFja2FnZTpTNFZlY3Rv
cnMnOlxuXG4gICAgZmlyc3QsIGludGVyc2VjdCwgcmVuYW1lLCBzZXRkaWZmLCBzZXRlcXVhbCwgdW5pb25cblxuXG5UaGUgZm9s
bG93aW5nIG9iamVjdCBpcyBtYXNrZWQgZnJvbSAncGFja2FnZTptYXRyaXhTdGF0cyc6XG5cbiAgICBjb3VudFxuXG5cblRoZSBm
b2xsb3dpbmcgb2JqZWN0IGlzIG1hc2tlZCBmcm9tICdwYWNrYWdlOkJpb2Jhc2UnOlxuXG4gICAgY29tYmluZVxuXG5cblRoZSBm
b2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZyb20gJ3BhY2thZ2U6QmlvY0dlbmVyaWNzJzpcblxuICAgIGNvbWJpbmUsIGlu
dGVyc2VjdCwgc2V0ZGlmZiwgc2V0ZXF1YWwsIHVuaW9uXG5cblxuVGhlIGZvbGxvd2luZyBvYmplY3QgaXMgbWFza2VkIGZyb20g
J3BhY2thZ2U6Z2VuZXJpY3MnOlxuXG4gICAgZXhwbGFpblxuXG5cblRoZSBmb2xsb3dpbmcgb2JqZWN0cyBhcmUgbWFza2VkIGZy
b20gJ3BhY2thZ2U6c3RhdHMnOlxuXG4gICAgZmlsdGVyLCBsYWdcblxuXG5UaGUgZm9sbG93aW5nIG9iamVjdHMgYXJlIG1hc2tl
ZCBmcm9tICdwYWNrYWdlOmJhc2UnOlxuXG4gICAgaW50ZXJzZWN0LCBzZXRkaWZmLCBzZXRlcXVhbCwgdW5pb25cblxuXG5wYWNr
YWdlICdncHJvZmlsZXIyJyB3YXMgYnVpbHQgdW5kZXIgUiB2ZXJzaW9uIDQuNS4zXG5wYWNrYWdlICdnZ3Bsb3QyJyB3YXMgYnVp
bHQgdW5kZXIgUiB2ZXJzaW9uIDQuNS4zXG5wYWNrYWdlICdnZ3JlcGVsJyB3YXMgYnVpbHQgdW5kZXIgUiB2ZXJzaW9uIDQuNS4z
XG5SZWdpc3RlcmVkIFMzIG1ldGhvZCBvdmVyd3JpdHRlbiBieSAnU2V1cmF0RGlzayc6XG4gIG1ldGhvZCAgICAgICAgICAgIGZy
b20gIFxuICBhcy5zcGFyc2UuSDVHcm91cCBTZXVyYXRcbiIsInBsb3RzIjpbXSwiZGF0YWZyYW1lcyI6W10sImVycm9yIjpudWxs
LCJlcnJvcl90cmFjZSI6bnVsbCwic291cmNlX2NvZGUiOiJsaWJyYXJ5KEZsdWZmdGFpbClcbmxpYnJhcnkoU2V1cmF0KVxubGli
cmFyeShTZXVyYXRXcmFwcGVycylcbmxpYnJhcnkobW9ub2NsZTMpXG5saWJyYXJ5KENsdXN0QXNzZXNzKVxubGlicmFyeShkcGx5
cilcbmxpYnJhcnkoZ3Byb2ZpbGVyMilcbmxpYnJhcnkoZ2dwbG90MilcbmxpYnJhcnkoZ2dyZXBlbClcbmxpYnJhcnkoU2V1cmF0
RGlzaylcbmxpYnJhcnkoYW5uZGF0YVIpXG5zZXQuc2VlZCg0MilcbiIsInBsb3RzX2h0bWwiOltdfX0seyJmaW5nZXJwcmludCI6
IntcImxhbmd1YWdlXCI6XCJyXCIsXCJjb2RlXCI6XCJcXHJcXG4jIGZ1bGwgPC0gcmVhZFJEUyhcXFwiQzovVXNlcnMvRmxvYXJl
YS9EZXNrdG9wL2NvcmViaW9pbmZvL2NvZGVzL2ZsdWZmdGFpbC9pbnB1dF9kYXRhL0dTRTIwMjM3OV9TZXVyYXRPYmplY3RfQWxs
Q2VsbHMucmRzXFxcIilcXHJcXG4jIGRpc2Vhc2Vfb3JkZXIgPC0gYyhcXHJcXG4jICAgXFxcIk5BU0ggd2l0aCBjaXJyaG9zaXNc
XFwiLFxcclxcbiMgICBcXFwiTkFGTERcXFwiLFxcclxcbiMgICBcXFwiTkFTSCB3L28gY2lycmhvc2lzXFxcIixcXHJcXG4jICAg
XFxcIkhlYWx0aHkgY29udHJvbFxcXCIsXFxyXFxuIyAgIFxcXCJlbmQgc3RhZ2VcXFwiXFxyXFxuIyApXFxyXFxuXFxyXFxuIyBt
ZXRhIDwtIGZ1bGxAbWV0YS5kYXRhICU+JVxcclxcbiMgICBtdXRhdGUoRGlzZWFzZS5zdGF0dXMgPSBmYWN0b3IoRGlzZWFzZS5z
dGF0dXMsIGxldmVscyA9IGRpc2Vhc2Vfb3JkZXIpKVxcclxcblxcclxcbiMgIyBIZXBhdG9jeXRlL0Nob2xhbmdpb2N5dGUgY29t
cG9zaXRpb24gd2l0aGluIGVhY2ggZGlzZWFzZVxcclxcbiMgbWV0YSAlPiVcXHJcXG4jICAgZmlsdGVyKGNlbGwuYW5ub3RhdGlv
biAlaW4lIGMoXFxcIkhlcGF0b2N5dGVzXFxcIiwgXFxcIkNob2xhbmdpb2N5dGVzXFxcIikpICU+JVxcclxcbiMgICBjb3VudChE
aXNlYXNlLnN0YXR1cywgY2VsbC5hbm5vdGF0aW9uKSAlPiVcXHJcXG4jICAgZ3JvdXBfYnkoRGlzZWFzZS5zdGF0dXMpICU+JVxc
clxcbiMgICBtdXRhdGUocGVyY2VudCA9IHJvdW5kKDEwMCAqIG4gLyBzdW0obiksIDIpKVxcclxcblxcclxcbiMgIyBEaXNlYXNl
IGNvbXBvc2l0aW9uIG9mIGVudGlyZSBkYXRhc2V0XFxyXFxuIyBtZXRhICU+JVxcclxcbiMgICBjb3VudChEaXNlYXNlLnN0YXR1
cykgJT4lXFxyXFxuIyAgIG11dGF0ZShwZXJjZW50ID0gcm91bmQoMTAwICogbiAvIHN1bShuKSwgMikpXFxyXFxuXFxyXCIsXCJv
cHRpb25zXCI6e1wiY2FjaGVcIjpmYWxzZSxcImxhYmVsXCI6XCJsb2FkX29iamVjdFwifX0iLCJyZXN1bHQiOm51bGx9LHsiZmlu
Z2VycHJpbnQiOiJ7XCJsYW5ndWFnZVwiOlwiclwiLFwiY29kZVwiOlwiIyBEZWZhdWx0QXNzYXkoZnVsbClcXHJcXG4jIGRpbShm
dWxsW1tcXFwiUk5BXFxcIl1dKSAjMzEyNTcgOTk4MDlcXHJcXG4jIGRpbShmdWxsW1tcXFwiU0NUXFxcIl1dKSAjMzAxMTcgOTk4
MDlcXHJcXG4jICMga2VlcCBvbmx5IHRoZSBjZWxscyB3ZSdyZSBpbnRlcmVzdGVkIGluXFxyXFxuIyBjZWxsc19rZWVwIDwtIGNv
bG5hbWVzKGZ1bGwpW1xcclxcbiMgICBmdWxsJGNlbGwuYW5ub3RhdGlvbiAlaW4lIGMoXFxcIkhlcGF0b2N5dGVzXFxcIiwgXFxc
IkNob2xhbmdpb2N5dGVzXFxcIikgJlxcclxcbiMgICBmdWxsJERpc2Vhc2Uuc3RhdHVzID09IFxcXCJlbmQgc3RhZ2VcXFwiXFxy
XFxuIyBdXFxyXFxuIyBsZW5ndGgoY2VsbHNfa2VlcCkgIzI1NTI3XFxyXFxuIyBzZXVyYXRfb2JqZWN0IDwtIHN1YnNldChmdWxs
LGNlbGxzID0gY2VsbHNfa2VlcClcXHJcXG4jIHJtKGZ1bGwpXFxyXFxuXFxyXFxuIyAjc2NlIDwtIGFzLlNpbmdsZUNlbGxFeHBl
cmltZW50KHNldXJhdF9vYmplY3QpXFxyXFxuIyAjd3JpdGVfaDVhZChzY2UsIFxcXCJDOi9Vc2Vycy9GbG9hcmVhL0Rlc2t0b3Av
Y29yZWJpb2luZm8vY29kZXMvZmx1ZmZ0YWlsL2lucHV0X2RhdGEvR1NFMjAyMzc5X2ZpbHRlcmVkLmg1YWRcXFwiKVxcclxcblxc
clxcblxcclxcbiMgIyMgcHJlcGFyZSBzdWItc2FtcGxlXFxyXFxuIyBmdWxsX3NtYWxsIDwtIERpZXRTZXVyYXQoXFxyXFxuIyAg
IHNldXJhdF9vYmplY3QsXFxyXFxuIyAgIGFzc2F5cyA9IFxcXCJSTkFcXFwiLFxcclxcbiMgICBjb3VudHMgPSBUUlVFLFxcclxc
biMgICBkYXRhID0gRkFMU0UsXFxyXFxuIyAgIHNjYWxlLmRhdGEgPSBGQUxTRSxcXHJcXG4jICAgZGltcmVkdWNzID0gTlVMTFxc
clxcbiMgKVxcclxcblxcclxcbiMgIyBQbG90IHRoZSBVTUFQIHJlZHVjdGlvbiB0byB2aXN1YWxpemUgY2VsbCBhbm5vdGF0aW9u
c1xcclxcbiMgRGltUGxvdChzZXVyYXRfb2JqZWN0LCByZWR1Y3Rpb249XFxcInVtYXBfaGFybW9ueV90LjBcXFwiLCBncm91cC5i
eSA9IFxcXCJjZWxsLmFubm90YXRpb25cXFwiKVxcclxcblxcclxcbiMgYGBgXFxyXFxuXFxyXFxuIyBMZXQncyByZW1vdmUgdGhl
IGJvdHRvbSBpc2xhbmQgdG8gZm9jdXMgb24gdGhlIHBvcHVsYXRpb24gd2l0aCB0aGUgaGVwYXRvY3l0ZS1jaG9sYW5nb2N5dGUg
YnJpZGdlLlxcclxcbiMgYGBge3IgcmVtb3ZlX2lzbGFuZH1cXHJcXG4jICMgUmVtb3ZlIGJvdHRvbSBpc2xhbmQgLSBhbGwgYmVs
b3cgLTYgb24gVU1BUF8yXFxyXFxuIyB1bWFwX2RmIDwtIGFzLmRhdGEuZnJhbWUoc2V1cmF0X29iamVjdEByZWR1Y3Rpb25zJHVt
YXBfaGFybW9ueV90LjBAY2VsbC5lbWJlZGRpbmdzKVxcclxcbiMgY29sbmFtZXModW1hcF9kZikgPC0gYyhcXFwiVU1BUF8xXFxc
IiwgXFxcIlVNQVBfMlxcXCIpXFxyXFxuIyAjY2VsbF9uYW1lc19rZWVwIDwtIHJvd25hbWVzKHVtYXBfZGZbdW1hcF9kZiRVTUFQ
XzIgPiAtNixdKSAjb3JpZ2luYWxcXHJcXG4jIGNlbGxfbmFtZXNfa2VlcCA8LSByb3duYW1lcyh1bWFwX2RmW3VtYXBfZGYkVU1B
UF8xID4gNCAmIHVtYXBfZGYkVU1BUF8yID4gLTEwLCBdKVxcclxcbiMgc2V1cmF0X29iamVjdCA8LSBzdWJzZXQoc2V1cmF0X29i
amVjdCwgY2VsbHMgPSBjZWxsX25hbWVzX2tlZXApXFxyXFxuIyBEaW1QbG90KHNldXJhdF9vYmplY3QsIHJlZHVjdGlvbj1cXFwi
dW1hcF9oYXJtb255X3QuMFxcXCIsIGdyb3VwLmJ5ID0gXFxcImNlbGwuYW5ub3RhdGlvblxcXCIpXFxyXFxuXFxyXFxuXFxyXFxu
IyBgYGBcXHJcXG4jIGBgYHtyIGZ1enp5X2NsdXN0ZXJpbmdfYW5hbHlzaXN9XFxyXFxuIyBTYXZlU2V1cmF0UmRzKG9iamVjdCA9
IHNldXJhdF9vYmplY3QsIGZpbGUgPSBcXFwiQzovVXNlcnMvRmxvYXJlYS9EZXNrdG9wL2NvcmViaW9pbmZvL2NvZGVzL2ZsdWZm
dGFpbC9pbnB1dF9kYXRhL3NldXJhdF9vYmplY3QucmRzXFxcIilcXHJcXG4jIHdyaXRlTGluZXMoY29sbmFtZXMoc2V1cmF0X29i
amVjdCksIFxcXCJDOi9Vc2Vycy9GbG9hcmVhL0Rlc2t0b3AvY29yZWJpb2luZm8vY29kZXMvZmx1ZmZ0YWlsL2lucHV0X2RhdGEv
c2hhcmVkX2NlbGxzLnR4dFxcXCIpXFxyXCIsXCJvcHRpb25zXCI6e1wiY2FjaGVcIjpmYWxzZSxcImxhYmVsXCI6XCJsb2FkX29i
amVjdFwifX0iLCJyZXN1bHQiOm51bGx9LHsiZmluZ2VycHJpbnQiOiJ7XCJsYW5ndWFnZVwiOlwiclwiLFwiY29kZVwiOlwic2V1
cmF0X29iamVjdCA8LSBMb2FkU2V1cmF0UmRzKGZpbGUgPSBcXFwiQzovVXNlcnMvRmxvYXJlYS9EZXNrdG9wL2NvcmViaW9pbmZv
L2NvZGVzL2ZsdWZmdGFpbC9pbnB1dF9kYXRhL3NldXJhdF9vYmplY3QucmRzXFxcIilcXHJcXG5cXHJcXG4jICMgR2V0IHNhbXBs
ZSBuYW1lc1xcclxcbnNhbXBsZV9uYW1lcyA8LSBjb2xuYW1lcyhzZXVyYXRfb2JqZWN0KVxcclxcblxcclxcbiMgRXh0cmFjdCBh
ZGphY2VuY3kgbWF0cml4IChTTk4pIGZyb20gU2V1cmF0IG9iamVjdFxcclxcbmFkal9tYXRyaXggPC0gc2V1cmF0X29iamVjdEBn
cmFwaHMkU0NUX3NublxcclxcblxcclxcbiMgUnVuIGZ1enp5IGNsdXN0ZXJpbmcgYW5hbHlzaXNcXHJcXG5mdXp6eV9jbHVzdF9h
bmFseXNpcyA8LSBGbHVmZnRhaWw6OmZ1enp5X2NsdXN0ZXJpbmdfYW5hbHlzaXMoXFxyXFxuICAgIGFkal9tYXRyaXgsXFxyXFxu
ICAgIHNhbXBsZV9uYW1lcyA9IHNhbXBsZV9uYW1lcyxcXHJcXG4gICAgbl9yZXBldGl0aW9ucyA9IDMwLFxcclxcbiAgICBhbGdv
cml0aG0gPSAxLFxcclxcbiAgIHJlc29sdXRpb24gPSBjKDAuMDEsIDAuMDUsIDAuMSwgMC4xNSwgMC4yKVxcclxcbiAgKVxcclxc
blxcclxcbiMgVmlzdWFsaXNlIGNvbmZpZ3VyYXRpb25zLCBzb3J0ZWQgYnkgdGhlaXIgRUNDIG1lZGlhbi5cXHJcXG5wbG90X2Vj
Y19ib3hwbG90cyhmdXp6eV9jbHVzdF9hbmFseXNpcyRlY2NfbGlzdCwgNSwgc2VsZWN0X2hpZ2hlc3QgPSBUKVxcclwiLFwib3B0
aW9uc1wiOntcImxhYmVsXCI6XCJmdXp6eV9jbHVzdGVyaW5nX2FuYWx5c2lzXCJ9fSIsInJlc3VsdCI6eyJ0eXBlIjoicmVzdWx0
IiwiY2h1bmtfaWQiOiJjaHVuay02IiwiY29uc29sZSI6IkNsdXN0ZXJpbmcgYW5hbHlzaXMuLi5cblxuUGVyZm9ybWluZyBjbHVz
dGVyaW5nLi4uXG5cbmV4ZWN1dGluZyAlZG9wYXIlIHNlcXVlbnRpYWxseTogbm8gcGFyYWxsZWwgYmFja2VuZCByZWdpc3RlcmVk
XG5SZWNvbmNpbGluZyBsYWJlbHMuLi5cblxuR2V0dGluZyBhbGwgdGhlIG1lbWJlcnNoaXAgbGlzdHMuLi5cblxuQ2FsY3VsYXRp
bmcgYWxsIHRoZSBtZW1iZXJzaGlwIGRlZ3JlZSBtYXRyaWNlcy4uLlxuXG5HZXR0aW5nIHRoZSBoYXJkIGNsdXN0ZXJzIGZyb20g
dGhlIHRoZSBtZW1iZXJzaGlwIGRlZ3JlZSBtYXRyaWNlcy4uLlxuXG5HZXR0aW5nIGFsbCBlY2MgaW5mb3JtYXRpb24uLi5cbiIs
ImNvbnNvbGVfc2VnbWVudHMiOlt7ImNvZGUiOiJzZXVyYXRfb2JqZWN0IDwtIExvYWRTZXVyYXRSZHMoZmlsZSA9IFwiQzovVXNl
cnMvRmxvYXJlYS9EZXNrdG9wL2NvcmViaW9pbmZvL2NvZGVzL2ZsdWZmdGFpbC9pbnB1dF9kYXRhL3NldXJhdF9vYmplY3QucmRz
XCIpIiwib3V0cHV0IjoiIn0seyJjb2RlIjoic2FtcGxlX25hbWVzIDwtIGNvbG5hbWVzKHNldXJhdF9vYmplY3QpIiwib3V0cHV0
IjoiIn0seyJjb2RlIjoiYWRqX21hdHJpeCA8LSBzZXVyYXRfb2JqZWN0QGdyYXBocyRTQ1Rfc25uIiwib3V0cHV0IjoiIn0seyJj
b2RlIjoiZnV6enlfY2x1c3RfYW5hbHlzaXMgPC0gRmx1ZmZ0YWlsOjpmdXp6eV9jbHVzdGVyaW5nX2FuYWx5c2lzKGFkal9tYXRy
aXgsIHNhbXBsZV9uYW1lcyA9IHNhbXBsZV9uYW1lcywgbl9yZXBldGl0aW9ucyA9IDMwLCBhbGdvcml0aG0gPSAxLCByZXNvbHV0
aW9uID0gYygwLjAxLCAwLjA1LCAwLjEsIDAuMTUsIDAuMikpIiwib3V0cHV0IjoiQ2x1c3RlcmluZyBhbmFseXNpcy4uLlxuXG5Q
ZXJmb3JtaW5nIGNsdXN0ZXJpbmcuLi5cblxuZXhlY3V0aW5nICVkb3BhciUgc2VxdWVudGlhbGx5OiBubyBwYXJhbGxlbCBiYWNr
ZW5kIHJlZ2lzdGVyZWRcblJlY29uY2lsaW5nIGxhYmVscy4uLlxuXG5HZXR0aW5nIGFsbCB0aGUgbWVtYmVyc2hpcCBsaXN0cy4u
LlxuXG5DYWxjdWxhdGluZyBhbGwgdGhlIG1lbWJlcnNoaXAgZGVncmVlIG1hdHJpY2VzLi4uXG5cbkdldHRpbmcgdGhlIGhhcmQg
Y2x1c3RlcnMgZnJvbSB0aGUgdGhlIG1lbWJlcnNoaXAgZGVncmVlIG1hdHJpY2VzLi4uXG5cbkdldHRpbmcgYWxsIGVjYyBpbmZv
cm1hdGlvbi4uLlxuIn0seyJjb2RlIjoicGxvdF9lY2NfYm94cGxvdHMoZnV6enlfY2x1c3RfYW5hbHlzaXMkZWNjX2xpc3QsIDUs
IHNlbGVjdF9oaWdoZXN0ID0gVCkiLCJvdXRwdXQiOiIifV0sInN0ZG91dCI6IiIsInN0ZGVyciI6IkNsdXN0ZXJpbmcgYW5hbHlz
aXMuLi5cblxuUGVyZm9ybWluZyBjbHVzdGVyaW5nLi4uXG5cbmV4ZWN1dGluZyAlZG9wYXIlIHNlcXVlbnRpYWxseTogbm8gcGFy
YWxsZWwgYmFja2VuZCByZWdpc3RlcmVkXG5SZWNvbmNpbGluZyBsYWJlbHMuLi5cblxuR2V0dGluZyBhbGwgdGhlIG1lbWJlcnNo
aXAgbGlzdHMuLi5cblxuQ2FsY3VsYXRpbmcgYWxsIHRoZSBtZW1iZXJzaGlwIGRlZ3JlZSBtYXRyaWNlcy4uLlxuXG5HZXR0aW5n
IHRoZSBoYXJkIGNsdXN0ZXJzIGZyb20gdGhlIHRoZSBtZW1iZXJzaGlwIGRlZ3JlZSBtYXRyaWNlcy4uLlxuXG5HZXR0aW5nIGFs
bCBlY2MgaW5mb3JtYXRpb24uLi5cbiIsInBsb3RzIjpbImlWQk9SdzBLR2dvQUFBQU5TVWhFVWdBQUEwZ0FBQUpZQ0FNQUFBQnZt
RGJHQUFBQkNGQk1WRVVBQUFBQUFEb0FBR1lBT2pvQU9tWUFPcEFBWnBBQVpyWXpNek02QUFBNkFEbzZBR1k2T2dBNk9qbzZPbVk2
T3BBNlptWTZacEE2WnJZNmtKQTZrTFk2a050bUFBQm1BRHBtQUdabU9nQm1PanBtT21abVpnQm1aanBtWm1abVpwQm1rR1pta0pC
bWtMWm1rTnRtdHBCbXR0dG10ditRT2dDUU9qcVFPbWFRWmdDUVpqcVFabWFRa0RxUWtHYVFrTGFRdHBDUXR0dVF0ditRMjdhUTI5
dVEyLysyWmdDMlpqcTJrRHEya0dhMnRwQzJ0cmEydHR1MjI1QzIyOXUyMi8rMi83YTIvOXUyLy8vYmtEcmJrR2Jia0pEYnRtYmJ0
cERidHJiYjI1RGIyN2JiMjl2YjIvL2IvN2JiLzl2Yi8vLy90bWIvdHJiLzI1RC8yN2IvMjl2Ly83Yi8vOXYvLy85Um1ZQ1JBQUFB
Q1hCSVdYTUFBQkowQUFBU2RBSGVaaDk0QUFBZldrbEVRVlI0bk8zZGozL2J4bm5IY1ZDeXdpQk52ZGdMbWNsWjA4NnV4YlpPMTNt
TG1COUxyY2JNNU1WT0lvNHlpZi8vUHhudURqOE9JQ1dCNHNQREEvRHpmcjNpU0NJT09JTDRFb2ZEQVlnU0FEdUwycTRBMEFjRUNS
QkFrQUFCQkFrUVFKQUFBUVFKRUVDUUFBRUVDUkJBa0FBQkJBa1FzRXVRRm5GVUdKemZPZm04NlpSdm5oYi96cUxSdmF2bnlwclpy
Q2ExaGZwL3FDOWliZUliYTdobFZYWjVMOUF1WUpCbURhZWNSOFBpMzUyRFpHY2pIU1JYdDIyclFwRDZiT2VtM1hKOGN0VnN5bW1E
c0JsK2tIWjJkNURxOWhZazlGbTRJSzBtUjY4YlRVaVEwRDJpUWJwK2tqYmRIbDZZSDZmUjJXVWNEWjZXSVZ2RWExdmY1Y2RwUysr
eG0rVE5hUlFkUDdjbFUwUDNyOTBDMHkzN3E2K2o2TUZMTTluSy9IVHVOa3kvZUJHQW1kM0lUYTNNUkc0MjVxVWY0N1JjNGsyYi84
SE5xNXh2ZGVLaVd0N2lzcm81NlJ0ZG5FYURaOG5xbTAyRlZsL0hlWDJ6Qlgxclp2UG9LcW0rTDNTY1pKQ3lneUM3dlV5akwrelBa
Y3JtMGFmcFJqVjRYaGJOcHJlVFpEOFBOd2FwUExoYW50cWZmdWMyek9vUzBrM2FiSjMyRC9OMGdrcVFmbGM1UFBQL1lMZHZiNzZW
aWN0cWVZdXJCY205MGVmVFRZV3l1disyQ0ZMK1p0SzlzLysrMEhXQ1FWckVVZnA5blg2MW15MGozYXlHVjhtYnVHelQ1REVibGlV
SDZaZng5Y1JzLzR2NHdhdjg1M3BuUTdyQnBmRkxYeHVhM3g5Y21CL1RQL3ZGcmJsTnhOaHNvelpVZm1kRE5vZThNdjRmc3IxRk1W
Ly9OYTlhL3VMOHBsMzZSais5TW04dWZYbXRrRC9mZkVFbjZSNzdlcHkrNkw4dmRKMWdrS2JaZGpweit4WDc1N20vdzNpVWJrSnBl
KytzS0ZrZU5HVWRFWFptRzRJMHl2NlFiczNuZGpJYnBOb3hWMWI0Qzd1TnBxOVZnalJLL08zZi84UE1oYktZci8rYVZ5MS9jZFVn
dWFha2ZWdnJoZXpQcXlLeCtRRlk3WDJoOCtTQ1ZCeWsyMDF1NnZLeTNzTlFSc3Q4SXo5Nm1mOFlGVTJlRFVFeTgxckVKMWY1Y2RZ
MDIzTTg4bzh2WEhvRy96VWV1ZU94U3BEeU9SU0xMdjVnSnF2Tk4zL05yNWEvdUdxUVJrbnhwV0RtNHhmS2wxanAvbjcvdjk4K2lh
b0wybUg5UXdlNUlCVmYyUzVJTGxYclhXRGVON3M3RC9Yd2xmMUN2eTFJZGg1bWc4dTM0SmxyUXVYRk03UG9iRFU1K1hWaURxM09O
cHhIOG9OVS9zRk01cy9YZTYxU0xXOXgxU0NkSlpVZytZWHlDZWRsa0g2TTh3UEp0VnFodzRJSHlkOUgyUjZzcU41TWF4cWtzbmht
RVkrVzQyRXlQYm1hbXRsSkJNbmZuNWFMdXlOSTYyM0FNa2pwd2RUeEowOWZ6UWhTeit5aGFXZTNqS3hwdDNZZ1UvL0w2czJUOUpz
N081WndiZ2xTM2dRcnpzdTQ0c1dzaDJhTG5hZXRPMU9uTFlMa3o3Y1NwUHI1SjdlNE80SlVGbHByMnVVdkVxUysyVjluZzkzV3lp
T2lQRUN6K3JGMWRraGwvMm8zcWx1QzVIY0tKTlg1MmhvYy9UVjlmUkYvWVYvZUlralZ6b2J5TmI5YTN1SnVEWkpmS0p0WDJkbVF6
Y24rZ1NEMXlUNjZ2ODJtNVhxRjM1UjlkT2xmSGx3a3EyL0sweWFMK0NnOTRFai9Zc05qSnI4K2RjYytabzd1My9vM3Q5ZWQ3QmZQ
ek8zQlRCcUhRWEdtMVphNk0walY3dS95TmE5YS91TDhiWDg5U1A1N21abGU4ZFcwNlA1TzYvWThNYTlGUTRMVUsvczdJZnRiKy9Q
amNzTFQ4bFZuNnAyUTlNNnVtcVA2WWZadlBVaEZsOWlvV3R4Snl3eUxjN0psajhUdzdpQjU4NjFNN0ZYTFc1eXJXLzRtNmtIeUM3
bjU1aWVReTBvVHBMN1o3eENoWTI4Y2d4MHRVeDBRWXdiZDJMTkxpUnRXazQwbytqRTJHNkg5ZCsxWXd1endCbysvc1Z1dlg5d3RZ
VksyNmJ4ZXNwTmY3d3lTTjkvcTl1MVZ5MXVjcTJHU3ZkR2tGaVMvME9yYjZoQWg4M3QwL1BTbjJIU29FNlQrMk5lRmZkT3lUYmVQ
dWRmN0FwWFBGNzNYclNDNWNUckpaZHh3SUhuYjg4WEI2RmFRaWdNVjZabnZhNzQ0RkIwTGtqc3ArdkRpN2lsMXpCZUhncHVmQUFJ
SUVpQ0FJQUVDQ0JJZ2dDQUJBZ2dTSUlBZ0FRSUlFaUNBSUFFQ0NCSWdZS2NnemNxTGE1SnNtRTErNFVUbGw5eHFZcTdDOGE4YVdI
eit1bmpOWEFDNzRjNVVacEpxb1Z0OGJXK250NzQ4Ky9mcWl6Y3JLM1hud2o0NGJWaXhyZDRGdWtjdVNQbXpLZXlsZkpWZkN1dEJt
aDNkR2FUWlVmTk5jQjVGL3BYc3hmTHMzMnN2M3ZLMm1vMEJOL1A3b0drMnRua1g2S0RkZ3VSdGNjdHg5UGpuSlBucDFJeFdyZnhT
TWh2MnpYT3dkeSs1ZlNGM21kK3d2TG03UDJyRGNiU05nN1RGdU54dDNnVTZTQ3hJK1kxOXZLdE9LMWQvWHNiUmcxZjVIbUwxSWpL
MzY3VVhZby9TelgwV0hiMXllNlI1Yk82ZWtIMTVwNi9razVoZnphME9zaGUvKzlqY3R6Nlh2ekIxZDZCYlc1NzkrNys2RjgyMEQr
MU16Rkl2dk4rem1ib2xlclUrOXhkUkx0dk85QWRiTWZ1NGdHSnY2L2FEYnU3Mnh2dlBranZlUmJZNjBHRlNRU3B2Vi9ldTlrczJx
V25vUFRoMUcxdDJoNFN6ZlBzNnRwZURteUFkeCs2MkNKdUNOSStqL0VYWGJpeHUrcDIvNEFXcHNqd3ZTSXR5Sm1hcFY0dTFtZnBC
bXVkM2FkaXc3REpJeFUzei9TQWR1eXZscTI5MDg3dklWOGN1SHdWYUpuS01sRzRXbFZiWmVoUE5Yb0pxN3hkdnRxWkYvUGdxdTYy
d2V5ckRLRDlHaWo2OVduMVQyU1NMbzR0MHN1ZjJKdlRtcCtGVmVWK3Y4b1d5dFZWZFh0bTBXMDNNTi84YmQyZGh1MVR2OTN5bXhm
ZUR2YXZDcGIxdHhJWmx1L25aZTRUNXk4cUM1T2FlN3BUOE43cjVYWlNyQTUwVktFaUxlSlRrdDhZMlFUcitOM2VuWWJkOW1RM1hi
Wkp1UXpRM0Jsa0xVcmFsVFFmbnJrQ3hrUEtGTWtqVjVaVkJjbjgzODNRenFmOXVaMW9FS1h2Vlg0UTNXUjRrZXh2VmNsbFprTEo1
dlB2dXl6aTY0MTJVcXdPZEpkVzB1eU5JYmdzdmV0SHNsZDNtaGp4bFo1WUxrdHVzelZhMklVZzJKUFBLaTBiNVFobWsydktLSU0y
TDZMdVoxSDh2bHVqUDJWK0VOMWtlcEZsMkU4aHFrT3pCWWRaNWVkZTdLRllIT2t2K0dPbkhSeGVWWCt6L2F4dTJ2V0dWT1p6cGQ1
RFNwdW9uZi92K2wvR2Q3eUpmSGVnczhWNDdlNGUzeWkrR2F5U1pQVlZ4TXVYdFg4ekR3R3BCY2srNU0vY3dyalMwNm8yaVdwQnVh
dG9WeS9PYWR2a2h2WnRKL2ZkNmtEWTA3ZGFDVkRidHlscjdjNjhjSTkzNEx1enFRR2Z0NFR6U3FQYUxlOVgxZGcrelRlL1RxMlQx
VGJybHo3d2VPdHZaTUVwc1owUGEybm5tcGk4bThRL1RLNXZnRFowTjN2SXFuUTMydVh2bFVWajk5MnlKMlp6TnJjVEhOeXg3dmJP
aHJIVWVwS0c5ZDdIcDJidmxYWlNyQTUwbE03TEJIYmVYb3h5cXZ4anpEZDNmcnVkNDVBZnBremliV3pGOU9ZblhjVndKVXZtQ2Q0
NjBzanp2aEd6V2xodmxlOGJhN3k1STFlNXZXMnpEc3ZNZ2VjK01yUzYxNk9IMjMraUdPWldyQTUwbEY2VGsra1ZjRHErci9HS2to
d0VQZnFpY2tEVVBDRitlUnNOZi9XT2tkRHY3cC95dXdJL01NOE84U1JibHFjeEtrSW9YL01FR2xlVjVJeHNXMlJQSDh5Wm05ZmRW
dnNSc283N01IeCs5WWRsRmtPeFVmN1ROMHJ6VzJkenR5ZGVYcHNGMzY3c29WZ2M2aTlIZlFyS09FaHdvZ3JTelJmekJsWGwwQzMw
Rmg0d2c3WXhESEJBa0NSemlnQ0FCRWdnU0lJQWdBUUlJRWlDQUlBRUNDQklnZ0NBQkFnZ1NJR0NYSUJGQ0lFT1FBQUVFQ1JCQWtB
QUJCQWtRUUpBQUFRUUpFRUNRQUFFRUNSQkFrQUFCQkFrUVFKQUFBUVFKRUVDUUFBRUVDUkRRSUF6THo0ckhKRXdyOTBFa1NFQ21R
UmlteGZOR1p1WkJFdVhEK0FnUzFuejQ0WWR0VjJGTmlEcmRHWWJsT01xRHRCeWJaenFVejBRaVNLajc4RU45U1FwU3B6dkRNQjh1
UHNxQ1pIK3dhV3BZMXIyRmNCcTlZK3EweDQxcTd3dTRoekIxYXJCWEtZSTBkdzkydEVHeTk0Mi9zNmpHRFlRNkVhUTl1RWVRaXVj
QUVhUSsxK2xlOXI2QWV3aFRwL3Z1a1JxV3hZSFJseU10eDBoZWtMWS9Sa0tIOVdZM3FhUFh6Z3NTdlhZSHBUOUJDbUdiSUNWVHpp
TWRFSUswamFaQldrMU1IOE0waXNvY0VTUWd4MWc3ZElqZXZTUkJRb2NRSkVBQVFRSjZqU0FCQWdnU0lJQWdBUUlJRWlDQUlBRUND
QklnZ0NBQkFnZ1NJSUFnQVFJSUVpQ0FJRUhVZGlQVStvTWdRZEsyWXoxN2d5QkIwUGFqcHZ1Q0lFRVFRUXBkRnIxRWtFS1hSUzhS
cE5CbDBVK0htaU9DQkZrSG1pT0NCRWdnU0lBQWdnUUlJRWlBQUlJRUNDQklnQUNDQkFnZ1NJQUFnZ1FJSUVpQUFJSUVDQ0JJZ0FD
Q0JBZ2dTSUFBZ2dRSUlFaUFBSUlFQ0NCSWdBQ0NCQWdnU0lBQWdvVGVDM0ZERm9LRXZndHlpekNDaEo0TGM5Tktnb1NlSTBpQUFJ
SUVTT0FZQ1pCQXJ4M1FFUVFKRUVDUUFBRUVDUkJBa0FBQkJBa1FRSkFBQVFRSkVFQ1FBQUVFQ1JCQWtBQUJCQWtRUUpEUWV3eGFC
WGJIWlJUQTdyaXdEeEJBa0FBQkJBa1FRSkFBQ1hRMkFCTG8vZ1k2Z2lBQkFnZ1NJSUFnQVFJSUVpQ0FJQUVDQ0JJZ2dDQUJBZ2dT
SUlBZ0FRSUlFaUNBSUFFQ0NCSWdnQ0FCQWdnU0lJQWdBUUlJRWlDQUlBRUNDQklnZ0NBQkFnZ1NJSUFnQVFJSUVpQ0FJQUVDQ0JJ
Z2dDQUJBZ2dTSUlBZ0FRSUlFaUNBSUtIM2VCb0ZzRHVlandUc2ppZjJBUUlJRWlDQUlBRVNPRVlDZHNjZUNSQkFrQUFCQkFtUXdE
RVNJSUdSRFVCSEVDUkFBRUVDQkJBa1FBQkJBZ1FRSkVBQVFRSUVFQ1JBQUVFQ0JCQWtRQUJCUXUvcEdDSTBqYUtUSy9mamFsTCsz
S2dzMEQ0ZGcxWm5KMWVyeWREK3VKcWtLWnFXU1NKSTZBQWRsMUVzeDJkSk1qOTZiWDVlZkhTZS9kT3NMQTVRaUdiVWRuUUV5ZWJH
cG9rZzRXNUJtbEhiMFJFa3V6UEtndVEzN1NKanozVkQ1NFRaYUxlazRoZ3BDOUxJL1RhbHN3RzNVUmtrRmIxMi9oNXBPUjZtZXlW
M3ZOU2tMQTZPemlDRnNNMHhrZzBWeDBpNEdVRzZpZDlyUjVCd0I0SjBvMmw1SHNrMDdUaVBoRnNRcEp0Tm8yaG9ldXhHSmtsME51
QldoNW9qeHRwQjFvSG1pQ0FCRWdnU0lJQWdBUUkyaE9IZHovY3ZDeHltZWhpdS94UkZSLy80N05sOXlnSUhxeGFHUlR6NFEzejB3
eVE2Mjc0c2NMaHFZWmhHWjh2eDBldEY3SjB1YWxvV09GelZNSmdRNWY5dFd4WTRZQVFKRUZBTncycmltbmJ6aUtZZHNJVk5uUTJE
ZjQ4SDU1c252NjBzd0JDaDNPTFVYRVArb0VtT0NCTFdNR2kxOFA3dHE0Wm5aQWtTYXJpTUluUlo5QkpCY3BaUGZwdDVTSzhkdGtl
UUhCZWtPSXFPQ1JMdVEyV09XcnVMMEdyYXBQZWJJR0dkemh5MWRWKzdSVHk4ZDFsQWxUYnZ0TXJJQnZSR20wR2FNYklCZmRGR2tM
SmV1eWlLUmx1WEJYUnE0UmdwNy83KzVPWDJaUUdkVk54RWYxOWxnVUIwUE5abFgyV0JRSUlIcVJ6V3dNZ0c5QWRCQWlSd2pBUUlJ
RWpBN3RycGJIamoybmN4SXh2UUU2MEVhUlpsSGpHeUFmM1FScEJXazhGWGs4SDU5WmdiUktJMzJoalpNRDU2UFUxRHhGMkUwQ1Bo
cjBkeXQrSWFNZm9iMk01YTArN2NYSXRFa0lDdDFNS1F0dW4rTVI0OC9RdE5PMkFiOVRCYy91YjFJbTU0WXp1Q0JHUTJocUhobzhZ
SUVwRHh4OXA5OXJUSkxVODJsZ1gwQ3R4cnR4eEgwY05YOXlzTHFCWCtQTkwxaXlnYU5OOHRFU1IwUUV0ajdVNmI3NVlJRWpxZ3JT
dGszMzhiUjhmUHVVRWtlcUxGUzgzZnZvZzRJWXVlYURGSWI1NFFKUFJGVzBHNmZtR2FkdmNyQzZqVFNwQldseDlIMGFPTGU1VUZW
QXJmL2YzMlNSUU5HdlV6ckpjRnRPS0VMTkFSREJFQ0JIQVhJVUFBUVFJRUVDUkFBRUVDQkJBa1FBQkJBZ1JVdy9EbWN6UEVianA0
ZG8reXdBR3JoT0hyYUdCdWVuSVpSOE90eXdLSHpBL0RQRHB5byt4V0V4N0dER3pEQzBNYW4veU8zOXl5R05oS1pheGRjUkVTZDFv
RnRrS1FBQUdWcHQwZ3Y3L3FJcVpwQjJ6QkQ4T3M2R0tZTmVxMkkwam9oTkNQZFZtT3N5VE5HdDJ5Z1NDaEU4SmZJV3R1bi8vd0Mz
T1piSk43NkJNa2RFRXJqNzc4OXVNb3pkTExaaGY0RVNSMFFJdTM0d3BRRmdpRUlBRVNXbmdZTTROVzBVUEJIOGJNb0ZYMFVQQTlF
b05XMFVQQmo1RVl0SW8rQ2g0a3h0cWhqd2dTSUNIME1SS0RWdEZQb1h2dEdMUUszQk9EVmdFQkRGb0ZCREJvRlJEQVdEdEFBRUVD
QlBqZDMxLytQbTNTdmY4NTRUd1NlaVg0b3kvVDlMZ0lFU1QwUitnVHNnUUpmZFRPRUNHQ2hKNGhTSUFBZ2dRSUlFaUFBSUlFQ0dn
aFNGR0pJS0V2Z2wrUDlPVVhwZDl6UFJMNkl2aGRoQUtXUlUrRjJHZzFJa2lRRktRWnBSRkJncUF3Qi9ZYUVTUUlJa2loeTZLWENG
TG9zdWdsZ2hTNkxIcUpJSVV1aTE0aVNLSExvcGNJVXVpeTZDV0NGTG9zK3VsUWMwU1FJT3RBYzBTUTBIOE1XZ1YyMThMRG1NT1ZC
UUlKZm1GZjBMSkFJQVFKSGFTdnM0RWdvWHNVZG44VEpIU095aE95ZERhZ2ExUUdpZTV2ZEkzT0lJVkFrQ0NJSUlVdWkxNGlTS0hM
b3A4T05VY0VDYklPTkVjRUNaQkFrQUFCQkFtOXgza2tZSGRLUmpaTW8ramthc1BQQkFtZG9HU3MzZXprYWpVWnVwK25vL1MvTWtr
RUNSMmdJMGpMOFZtU3pOMWp4eFlmbldmL05Dc0xLS0FqU0RZM05rMXBuazZxVHg4alNPZ0FIVUdhdTBmSzJpRE5odlBpbVpqMita
aDdyaHNnUUZXUVJ1Ym5hVFNzN0pZSUVqcEFWWkRzSHNuMk0yUS9OeWtMS0tBalNQNHgwc3gwM2hFa2RJdU9JUG05ZG03djlCbTlk
dWdVSFNka3ArVjVwTlZrWk04ck5TNExhS0JqaU5BME1uME1Oa1NyQ1NNYmdFMFlhd2NJSUVpQUFJSUVDQ0JJZ0FDQ0JBZ2dTSUFB
Z29UZTAzRWVhVDlsZ1ZCMGpHellVMWtnRUIxajdmWlZGZ2lFSUFFQ0NCSWdnV01rUUFLOWRrQkhFQ1JBQUVFQ0JCQWtRQUJCUXUv
UjJRRHNqdTV2WUhlY2tBVUVFQ1JBQUVFQ0JCQWtRQUJCQWdRUUpFQUFRUUlFRUNSQUFFRUNKREN5QVpEQVdEdWdJd2dTSUlBZ0FR
SUlFaUNBSUVGVWlBUDdiZEhaZ0s0SjB0VzhKYnEvMFRWaFRuNXVoeE95NkJ5Q0ZMb3Nlb2tnaFM2TFhpSklvY3VpbHdoUzZMTG9K
WUlVdWl4NlNXT1E2UDVHOTJqTkVYc2tkSXU2SEJFa1FBSkJRZ2V4UndwYkZ2M0VNVkxnc3VnbGpiMTJCQW1kUTVCQ2wwVXZFYVRR
WmRGTEdvUEVDVmwwanNvZ2NZVXNPa2Rqam9JZ1NCQjFvRGtpU0lBRWdvVGU0eGdKMkIyOWRzRHVPSThFQ0NCSWdBQ0NCQWdnU0lB
QWdnUUlJRWlBQUlJRUNDQklnQUNDQkFnZ1NJQUFnZ1FJSUVpQUFJSUVTR0QwTjdBNzlraUFBSUlFQ0NCSWdBQ0NCQWdnU0lBQWdn
UUlJRWlBQUlLRUR0SjNwMVdDaE81UmVPOXZnb1RPQ2JQUmJvY2dvWE1JVXVpeTZDV0NGTG9zZW9rZ2hTNkxYaUpJb2N1aWx6UUdp
ZXVSMERrcWc4VHprZEExT29NVUFrR0NJSUlVdWl4NmlTQ0ZMb3RlSWtpaHk2S2ZEalZIQkFteURqUkhCQW1RUUpBQUFRUUpFRUNR
SUlwanBMQmwwVS8wMmdVdWkxN2lQRkxvc3VnbGdoUzZMSHFKSUlVdWkxNGlTS0hMb3BjSVV1aXk2S2REelJGQmdxd0R6UkZCQWlR
UUpFQUFRUUlFRUNSQUFFRUNCQkFrUUFCQkFnUVFKRUFBUVFJRUVDUkFBRUVDQkJBa1FBQkJBZ1FRSkVBQVFRSUU3QlFrNE1DSkJH
bHZxRlJEMUttWkFIWFMrTGFwVkZQVXFSbUNwSWpHU2xHblpnNDFTRURYRUNSQUFFRUNCQkFrUUFCQkFnUVFKRUNBemlBdFB6dHZ1
d3E0cCtWNDJIWVYycUF5U012eGc1ZHQxNkZtT1k2aXM3WXJVVE9QOU5YSnJDaDFRUXF4b2pRR2FUayt1V3E3RGpYejlJT1lLdHRD
RnZGWjh1NWQyN1dvU1QrN1MyMmZYcEFWcFRCSUNuTzBtb3dTa3laVkZadU8ycTdCT3ZQWkxUNVMxaTRQc3FJVUJtbWVmdk9ibHBT
aXpYWTVOaTJEMVVUVFBzbUdlNXF1SmtWMXN0K0JibVhwRVdaRktReVMyUlZQMHc5a0VhdlpSRllUVTVYbHYvdzlWclNOcE90b2R2
VGFmdTlvOGY2L3pYZmZWRStGckNBclNtT1FrbG1VdnU5MDF6UlEwMGFZUmVtMzJ1emthcXBuTDJtL2IweXVGYTBtUjF1Rmdxd29s
VUZhVGV6MnFxbU5NRXViQnVubnNQak42N1pyVXBwRmRzdlF0Sm9zdC85V0pNU0tVaG1rNVBwN0V5UjFSNjJKcmlCbC9ZajZUcnBw
MnlXRldGRTZnNVIrcTMydjc0dE4zM2Z0TkRxNTBsYW5wR2hSS0xML0ZhVTFTTXE2bzR4RnJLa2owWm5yVzAyR29uNml6TjVYbE5Z
Z0FaMUNrRzZqNy9CREo1WHJLV3lsdEFScHJxMHRZQ2djODhkNmFpcHdwYlFFNlhLdFZmMC9yZmVQclk5VmFyOU9yS2VHUWxkS1M1
RFNJL25xRmpJN2Z0WlNWWExySDBYN2RXSTlOUlM4VWxxQ05ELzVxZkpkTzJ1L2YyeHR6SitDT3JHZUdncGVLUzFCbWc0cmZhWWFQ
b3Y2bUQ4VmRXSTlOUlM2VWxxQ3RQaFAvK3lEanMraU91WlBSNTFZVDAwRnJsVDdRVXBiL1Vldjh4K1ZmS2RsZldQK21ML1c2K1JS
czU2eXowN1hlbXFuVXEwSGFSNk55cXVUM1JiUy9oRHJ2RytzSFBQWGZwMThTdFpUOGRscFdrOHRWYXJ0SU9YWG51WkorbHpGbWIy
eWIwem5tRDhkNjhuLzdOU3NwN1lxMVg2UTdOQjJUVmVuSlg3Zm1KSXhmMTc3VncvL3MxT3ludHFyVk50QnluZTdjMVgzdzZuMWpi
V3UwdjdWUStkbjEwNmxXZy9TSW5hM3BtaS9jZTJwOW8yMXJ0YitWVVBuWjlkT3BWb1BVakp6WHgzNnJ1TFRrNlJxKzFmUkxSRlVm
bmJ0VktyOUlLVXRXZk1Wb3V2RHNQUWt5Vyt1TEo0ODFMT21WSDUyclZTcXZTQ1Z4ODh6TmRkNTFvN3BWZlNOR2RyYVVCby91NVly
MVZxUS9PTm5jKzJwaHM5QzZURjlvcTBOcGZHemE3dFNiUVZKNC9HenhqcmxOTFdoVks2bnRpdlZYcEQwblQvU1dLZUNvamFVeXZY
VWRxVmFhOXI1eDg5YStxRTAxcW1ncGcybGREMjFYS25XZ3VRZFA2dnBoOUpZSjQxVXJxZVdLOVZlcjUydTQyZEhZNTAwVXJtZTJx
MVVpK2VSTkIwLzV6VFdTU09WNjZuVlNyVjVRbGJSOFhOQlY1M1M0NkxLM1g4VjNGUWtvMnM5WmRxc1ZLc2pHeFFkUHhjMDFXazVI
cTBtWHBJVTNGU2tvR2s5RlZxc2xJSWhRcmlKdlZCM1dpU3AvWXRQY1NPQ3BOUDdLL09BUU5zUGxTZUpIR2xHa0ZSYXhHbHIvKzNZ
alIyYnFycXBDRFpxTzBoNkRwOUxHdXIwL3QxVmVaZkR0eityekpHRzliU21yVXFGRGxLdEgwckY0YlBHT3JtYjRKVDNDOVV3N2x2
bGV0SlNxY0JCcXZWRHFmaWExVmluTkVodng1VWt0VS9sZWxKVHFjQkJxdlpENmZnc05OYkpXTG9rcWVsalZybWUxRlFxWEpEVys2
SGEveXcwMXNsdzdSVTl1eU9WNjBsWHBZSUZhYjBmcXYzUFFtT2RqRVhzMml0YWtxUnlQU21yVk1BOVVxMGZTc1BoczhZNlpkZW96
ZHcrU1VmRFR1VjYwbFdwZ01kSXRYNG9GVFRXS1RIUGJGeDg5SlUvT0todEt0ZVRxa3FGREpLNmZpaVZkVnI5K2UveGFEa2VtUWR4
NjlnZkpTclhrN0pLQmUyMTA5WVBaYWlyazczRTB6VDNkVDB1VnQxNk1oUlZLbUJuUTlyb1YvTHRrZE5ZSjN2dTFWd0xrTjJFUUFP
VjYwbFpwVUlGS2V1STB2UEdFNTExU3V5ejVwS1psbnZTR3lyWGs3WktCUXBTMFJHbFl6OXNLYXpUNmsrbWYyRTZ6Sy8yVkVIaGVs
SllxVUJCVXRnUmxTaXNrOWtSbldtN2dsdmhlbEpZcVJCQld2MzU5VUpiUjVUQ09ybmRVWnFsa1pwYlhLbGNUem9yRlNKSTdsRTF1
anFpRk5acG5nMWpUamNPTmQrekd0ZVR6a29GYWRxWmM4N0tPcUkwMXFrWXhyelFjSDFDUnVGNlVsbXBJRUV5L1ZDNk9xSjAxbW1s
cDhsZjBMaWVORlpxMzBFcSs2SDBkRVFwckZQMkxIdGRTVks0bnBSV0t0bC9rRFQyUXltczArcE5iSk0wVjNSNHBIRTlLYTFVc3Vj
Z2FleUgwbGduWTJHVE5CK2Erek5vb0hJOXFheVVzOWNnYWV5SFVsaW41ZGcwOXUzMU5STTFqUldGNjBscHBaejlOdTAwOWtPcHE1
TjVWTzA4T3JreWVWSXkzc1ZRdDU0TWxaV3k5bnlNcE92bzJkRldKOXRLMFRMU3hhTnRQVmtxSzJYc0xVZ2ErNkUwMWltTmtIdlVu
S0k2cVZ4UEtpdFYybCtRRlBaRGFheFQ5dkRUUEU4cTZGeFBHaXRWMm1QVFRscy9sS0d4VGpPN1llanEwTlc0bm5SV0tyZWZJR25z
aDlKV3ArdUw3SWZWSkRwTDlEeHJTTnQ2c2xSV3FtSXZRZExZRDZXdFRzdHgyVUtaS2hyc29tMDlXU29yVmJXWElHbnNoMUpYSjZW
SHplcldrNkd5VWxYN0NKTENmaWlOZFNxVDlIOTZIdXVnY0QwcHJWVE5Qb0trc0I5S2FaM3k4L1I2dm1vMXJpZWRsYXJaUzlOT1l6
K1V4anE1Sk0wMURXSld1WjUwVnFwS05FaDVSNVNtZmlpTmRTcVlKQ25Ka2NyMXBMSlNtMGtHeWV1SVV0TVBwYkZPbm5RTDBaRWps
ZXRKWmFWdUlMcEgwdGdScGJGT0hqV25SVlN1SjVXVjJrejJHRWxqUjVUR09tbWtjajJwck5SR3dwME5PanVpOU5WSkk1WHJTV1ds
TnBIdXRkUFlFYVd4VGhxcFhFOHFLN1dCZVBlM29vNm9nc1k2YWFSeVBhbXMxRHI1ODBocU9xSThHdXVra2NyMXBMSlNhL1p3UWxa
TlI1UkhZNTAwVXJtZVZGYXFMdWlEeG9DK0lraUFBSUlFQ0NCSWdBQ0NCQWdnU0lHdHZ2MDRpbzZmMy9qNjExSDB3V25EeTZrWG43
L083MUoxZzFuV2NXd2V5b1Y5SWtoaExlTEllbnpENi9QMHRROXV6WVpuZG5SM2tOd0lHNEswYndRcHFPVTRldnh6a3Z4MEd0MXdz
ZWY4cGhjMk1VRzZZNHJzWmlFRWFkOElVbEI1VTh2ZG91MzZOSW9lWE5pYmlINzNjVFI0NWk2N09mckI3bVF1NDJqdzFENlZ6dnpt
bms4M25FVkhGOGxsMmpoTUp6Wm4vS09SZTNsOVR0bnlqdjVxbCtpQ2xCVk1sejY2ak5NZjVuSDB5TVRNbEg1NHNibkdhSVlnaGJT
YTVQdVFkK2wvYzl2TVM5dGVOaEwydVQ5bGtHYnVUOVVnSGNmcERpWjc1Y3dMMG9ZNU9iTjBacVp4WjRPVUYweUQ5RWxhWVBBZnNi
dGFicEdYeHYwUnBKQXFkNVJLTi9yblp1czJOejJNaGlZNlE5ZTBNOWxZamdjdmsrdEpMVWhtNzVLRzhjTGQ2YTA0UnRvNEp5dWR3
dTc4VEpES2dtbHluaWVYWmdTYnUrWGlJQzM5SmxaK25ZSnlCQ21rU3BBV2J0T2REczdkanNxK21BZkpqWGMyay9oQnl2Wm43Nzc3
TW82OElHMmNrMldtTU0zSjdCZ3BLMmluWDQ3dEU0MU42VkUrS2U2TklJVlVDMUordDdZeUswV1EzSDF6VnJWakpOdHhrSFg4VllL
MFlVNldtMkp3Ym9OVUZMVFJjWFdabXN3NnRPMTJRWkJDS28rUmZueDBjYzhnTGNmUkozLzcvcGR4NHlDWjl0c3Y0NUZYa0NESkkw
aEJsU2RJemNGTDJTQmJDMUxadEV1bWVXdk5UZVpTVXpsRzJqZ250endiM0ZuMHorT1JWN0FhcEN5RzJBbEJDcW84anpTcWREYXNC
YW5zYkVpbWtlM3FMb00wdkRJZDFxWm56L2JUVlRzYk5nWEpYUnBYRnF3R0tXMzZ2VXpTWlhHTXRBdUNGRlkrc3NGc3hGNm45VnFR
eXU1dk85Z2hlbkJhTnZMY0syNmF0ZTd2VFVFeVN4MTVCYXRCU3JLMkhhZHNkMEdRQXJ0K0VSZGo3UmJsYWRTMUlOa1RzbiswRy91
UGNmVG8xN0t6d1o1OGZXa2FmTXZUYVBpcjIwMnR6OG5LdStKc2s3SW9XQXVTTFgzTDhEODBRSkEwWTJSUFp4QWtuUmJ4QjFmSmFy
ck55RHUwaVNEcGxCM1FLSDA4SGRZUUpLVldMNkpvOEpnY2RRVkJBZ1FRSkVBQVFRSUVFQ1JBQUVFQ0JCQWtRQUJCQWdRUUpFQUFR
UUlFL0Qvd2Riemh5MmRybndBQUFBQkpSVTVFcmtKZ2dnPT0iXSwiZGF0YWZyYW1lcyI6W10sIm91dHB1dF9vcmRlciI6W3sidHlw
ZSI6InBsb3QiLCJpbmRleCI6MCwibmFtZSI6InBsb3RfZWNjX2JveHBsb3RzKGZ1enp5X2NsdXN0X2FuYWx5c2lzJGVjY19saXN0
LCA1LCBzZWxlY3RfaGlnaGVzdCA9IFQpIn1dLCJlcnJvciI6bnVsbCwiZXJyb3JfdHJhY2UiOm51bGwsInNvdXJjZV9jb2RlIjoi
c2V1cmF0X29iamVjdCA8LSBMb2FkU2V1cmF0UmRzKGZpbGUgPSBcIkM6L1VzZXJzL0Zsb2FyZWEvRGVza3RvcC9jb3JlYmlvaW5m
by9jb2Rlcy9mbHVmZnRhaWwvaW5wdXRfZGF0YS9zZXVyYXRfb2JqZWN0LnJkc1wiKVxuXG4jICMgR2V0IHNhbXBsZSBuYW1lc1xu
c2FtcGxlX25hbWVzIDwtIGNvbG5hbWVzKHNldXJhdF9vYmplY3QpXG5cbiMgRXh0cmFjdCBhZGphY2VuY3kgbWF0cml4IChTTk4p
IGZyb20gU2V1cmF0IG9iamVjdFxuYWRqX21hdHJpeCA8LSBzZXVyYXRfb2JqZWN0QGdyYXBocyRTQ1Rfc25uXG5cbiMgUnVuIGZ1
enp5IGNsdXN0ZXJpbmcgYW5hbHlzaXNcbmZ1enp5X2NsdXN0X2FuYWx5c2lzIDwtIEZsdWZmdGFpbDo6ZnV6enlfY2x1c3Rlcmlu
Z19hbmFseXNpcyhcbiAgICBhZGpfbWF0cml4LFxuICAgIHNhbXBsZV9uYW1lcyA9IHNhbXBsZV9uYW1lcyxcbiAgICBuX3JlcGV0
aXRpb25zID0gMzAsXG4gICAgYWxnb3JpdGhtID0gMSxcbiAgIHJlc29sdXRpb24gPSBjKDAuMDEsIDAuMDUsIDAuMSwgMC4xNSwg
MC4yKVxuICApXG5cbiMgVmlzdWFsaXNlIGNvbmZpZ3VyYXRpb25zLCBzb3J0ZWQgYnkgdGhlaXIgRUNDIG1lZGlhbi5cbnBsb3Rf
ZWNjX2JveHBsb3RzKGZ1enp5X2NsdXN0X2FuYWx5c2lzJGVjY19saXN0LCA1LCBzZWxlY3RfaGlnaGVzdCA9IFQpXG4iLCJwbG90
c19odG1sIjpbXX19XSwiY29kZUNlbGxSZXN1bHRzIjpbXX0=
RNOTEBOOK_RMD_STATE_END
-->
